---
title: Investigating the autism and ADHD prevalence in Chile through Bayesian prevalence
  analysis and clinical record data linkage
author: "Student 5526"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    number_sections: TRUE

---
    
<!--header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}
  - \posttitle{\end{center}} -->
  
<!-- Optionally include a page break. This will force the start
of the document to the second page -->


This dissertation is submitted for the degree of Master of Philosophy. The dissertation does not exceed the word limit for the respective Degree Committee.
Word count: xxx TODO

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "C:/Users/delat/OneDrive/MPhil Population Health Sciences 2022-2023/12 Dissertation")
```


```{r libraries}

#library(nleqslv) # Only needed for robince bayesian prevalence
library(janitor)
library(gridExtra)
library(readxl)
library(writexl)
library(viridis)
#library(wesanderson)
library(rgbif)
library(chilemapas) # For commune maps
library(leaflet)
library(plotly)
library(sf)
library(sp)
library(broom)
library(psych)
library(Hmisc)
library(poolr)
library(epitools)
#library(corrplot)
#library(caret)
library(mltools)
library(ggrepel)
library(rjags)
library(rstan)
library(posterior)
library(tidybayes)
library(bayesplot)
library(reclin2)
library(lubridate)
library(RecordLinkage)
library(dgof) # for statistical testing
library(fdm2id) # for predict that works for kmeans
library(ppclust) # for cmeans
library(factoextra) # for get_cluster_?
library(FactoMineR) # for MCA
library(tidyverse)

```


```{r import geographic data}

# Import region and commune boundaries
# https://data.humdata.org/dataset/cod-ab-chl
chile.adm1 <- st_read("04_Data/CHL_adm_humdata/chl_admbnda_adm1_bcn_20211008.shp", quiet = TRUE) #%>%
  #st_transform(crs = 32629)
chile.adm3 <- st_read("04_Data/CHL_adm_humdata/chl_admbnda_adm3_bcn_20211008.shp", quiet = TRUE) %>%
  mutate(commune_code = str_sub(ADM3_PCODE, start = 3, end = -1),
         commune_name = ADM3_ES)
#chile.adm3_old <- st_read("04_Data/CHL_adm/CHL_adm3.shp", quiet = TRUE)



# Get communes with health services
chile_communes_raw <- read_excel("04_Data/commune_by_health_service.xlsx") %>%
  clean_names()

chile_communes <- chile_communes_raw %>%
  mutate(commune_name = ifelse(comuna == "La Calera", "Calera",
                        ifelse(comuna == "Coihaique", "Coyhaique",
                        ifelse(comuna == "Paiguano", "Paihuano",
                        ifelse(comuna == "Pedro Aguirre Cerda", "Pedro Aguirre Cerda",
                        comuna))))) %>%
rename("health_service_name" = "servicio_de_salud") %>%
  select(commune_name, health_service_name)

# Create a number for each health service
health_service_lookup <- chile_communes %>%
  group_by(health_service_name) %>%
  summarise() %>% 
  #rename(health_service_name_long = health_service_name) %>%
  mutate(health_service_name_short = ifelse(grepl(" Del ", health_service_name), 
                                      str_sub(health_service_name, start = 23, end = -1), 
                                      str_sub(health_service_name, start = 19, end = -1))) %>%
  arrange(health_service_name) %>%
  rowid_to_column("health_service_code")

# Get region codes with region name abbreviations
region_abr_lookup <- data.frame(
  ADM1_PCODE = c(paste0("CL0", c(1:9)), paste0("CL", c(10:16))),
  region_name_abr = c("TPCA", "ANTOF", "ATCMA", "COQ", "VALPO", "LGBO", "MAULE", "BBIO",
                      "ARAUC", "LAGOS", "AYSEN", "MAG", "RM", "RIOS", "AYP", "NUBLE"))

# Put region, health service and communes together
region_service_commune_lookup <- chile.adm3 %>%
  merge(chile_communes, by = "commune_name", all = TRUE) %>%
  mutate(commune_code = ifelse(commune_name == "Antártica", "12202", commune_code),
         ADM3_PCODE = ifelse(commune_name == "Antártica", "CL12202", ADM3_PCODE),
         ADM1_ES = ifelse(commune_name == "Antártica", "Región de Magallanes y Antártica Chilena", ADM1_ES),
         ADM1_PCODE = ifelse(commune_name == "Antártica", "CL12", ADM1_PCODE),
         commune_name = ifelse(ADM3_PCODE == "CL01401", "Pozo Almonte", commune_name),
                        # For the Tocopilla in Tarapaca, use it's old name to avoid duplication issues
         health_service_name = 
           ifelse(ADM3_PCODE == "CL01401", "Servicio de Salud Antofagasta", 
           ifelse(ADM3_PCODE == "CL11201", "Servicio de Salud Aisén",
           ifelse(commune_name == "Isla de Pascua", "Servicio de Salud Metropolitano Oriente",
           ifelse(commune_name == "Los Alamos", "Servicio de Salud Arauco",
           ifelse(commune_name == "Los Angeles", "Servicio de Salud Biobío",
           ifelse(ADM3_PCODE == "CL06204", "Servicio de Salud Del Libertador B.O'Higgins",
           ifelse(commune_name == "Pedro Aguirre Cerda", "Servicio de Salud Metropolitano Sur",
           ifelse(commune_name == "Ranquil", "Servicio de Salud Ñuble", health_service_name)))))))),
         region_code = str_sub(ADM1_PCODE, start = 3, end = -1),
         commune_name_upper = toupper(commune_name)) %>%
  rename(region_name = ADM1_ES) %>%
  filter(!is.na(ADM3_PCODE)) %>% # Get rid of the communes that didn't match properly with health service lookup and were corrected above
  merge(region_abr_lookup, by = "ADM1_PCODE")
  
region_service_commune_lookup <- merge(region_service_commune_lookup, 
                                       health_service_lookup,
                                       by = "health_service_name", all = TRUE) %>%
  rename(region_name_long = region_name,
         health_service_name_long = health_service_name,
         health_service_name = health_service_name_short) %>%
  mutate(region_name = ifelse(region_name_long == "Región Metropolitana de Santiago", "Metropolitana de Santiago",
                       ifelse(grepl("Región de ", region_name_long), 
                              substr(region_name_long, start = 11, stop = nchar(region_name_long)), 
                       ifelse(grepl("Región del ", region_name_long), 
                              substr(region_name_long, start = 12, stop = nchar(region_name_long)), NA)))) %>%
  select(region_name_long, region_name, region_name_abr, region_code, ADM1_PCODE,
         commune_name, commune_name_upper, commune_code, 
         health_service_name_long, health_service_name, health_service_code,
         geometry)

# Aggregate to region level (no )
region_lookup <- region_service_commune_lookup %>% 
  as.tibble %>%
  select(-geometry) %>%
  group_by(region_code, ADM1_PCODE, region_name, region_name_abr) %>% 
  summarise() 

# Extract communes for the Araucania Sur and Norte health services
araucnorte_communes <- region_service_commune_lookup %>%
  filter(str_detect(health_service_name, "a Norte")) %>%
  as.tibble() %>%
  select(commune_code, commune_name)
araucsur_communes <- region_service_commune_lookup %>%
  filter(str_detect(health_service_name, "a Sur")) %>%
  as.tibble() %>%
  select(commune_code, commune_name)

```

```{r import standard population data}
chile_stdpop_raw <- read_excel("04_Data/pop_chile_2021_single_age.xlsx") %>%
  clean_names() 

chile_stdpop <- chile_stdpop_raw %>%
  filter(sex != 9) %>%
  rename("std_pop" = "pop_2021") %>%
  mutate(pop_prop = std_pop / sum(std_pop))
```

```{r import chile demog data}
# https://www.ine.gob.cl/estadisticas/sociales/demografia-y-vitales/proyecciones-de-poblacion
chile_regionpop_raw <- read_excel("04_Data/ine_estimaciones-y-proyecciones-2002-2035_base-2017_region_area_tabulados.xlsx", sheet = "Region summary 2021") %>%
  clean_names()

chile_regionpop <- chile_regionpop_raw %>%
  mutate(region_name = ifelse(region == "Aysén", "Aysén del Gral. Ibañez del Campo",
                         ifelse(region == "Biobío", "Bío-Bío",
                         ifelse(region == "Magallanes", "Magallanes y Antártica Chilena",
                         ifelse(region == "Metropolitana", "Metropolitana de Santiago",
                         ifelse(region == "OHiggins", "Libertador Bernardo O'Higgins", region)))))) %>%
  select(-region)

# https://www.ine.gob.cl/estadisticas/sociales/ingresos-y-gastos/encuesta-suplementaria-de-ingresos
# Income is from Supplementary Income Survey (ESI) (2021), data is from Instituto Nacional de Estadística (INE).
chile_regionincome_raw <- read_excel("04_Data/ingreso-medio-mensual-por-region-2010---2021.xlsx", skip = 2) %>%
  clean_names()

chile_regionincome <- chile_regionincome_raw %>%
  filter(ano == 2021,
         region != "Nacional") %>%
  mutate(region_short = ifelse(grepl("Región de ", region), 
                               substr(region, start = 11, stop = nchar(region)), 
                        ifelse(grepl("Región del ", region), 
                               substr(region, start = 12, stop = nchar(region)),
                        ifelse(region == "Región Metropolitana", "Metropolitana", NA))),
         region_name = ifelse(region_short == "Aysén", "Aysén del Gral. Ibañez del Campo",
                         ifelse(region_short == "Biobío", "Bío-Bío",
                         ifelse(region_short == "Magallanes", "Magallanes y Antártica Chilena",
                         ifelse(region_short == "Metropolitana", "Metropolitana de Santiago",
                         ifelse(region_short == "O’Higgins", "Libertador Bernardo O'Higgins", region_short)))))) %>%
  select(region_name, ingreso_medio_nominal)

```

```{r import school data}

chile_merged_raw <- read.csv("04_Data/Data_Chile_Merge.csv") %>% clean_names()

chile_merged <- chile_merged_raw %>%
  rename(sex_desc = sex,
         year = agno,
         school_code = rbd,
         school_check_code = dgv_rbd, 
         school_name = nom_rbd,
         school_region_code = cod_reg_rbd,
         school_region_name_abr = nom_reg_rbd_a,
         school_province_code = cod_pro_rbd,
         school_commune_code = cod_com_rbd_2,
         school_commune_name = nom_com_rbd_2,
         school_dept_code = cod_deprov_rbd,
         school_dept_name = nom_deprov_rbd,
         school_dependency_code = cod_depe, # has categories 1-6, no1 and no2 here are no1 in grouped
         school_dependency_code_grouped = cod_depe2, # has categories 1-5
         school_rurality_code = rural_rbd,
         school_operation_status = estado_estab, 
         teaching_code1 = cod_ense, # min = 10, max = 910, eg preschool, special education hearing impaired
         teaching_code2 = cod_ense2, # subject matter coding, 1-8
         teaching_code3 = cod_ense3, # age based coding, 1-7
         grade_code1 = cod_grado, # grade of schooling, 1-10, 21-25, 31-34, nests in teaching_code1
         grade_code2 = cod_grado2, # equivalent grade of schooling for adult special education, 1-8, 99
         grade_letter = let_cur, # refers to the class within the grade, close to start of alphabet is higher aptitude
         course_timing = cod_jor, # time of day, morning, afternoon, both, night, no info
         course_type = cod_tip_cur, # 0 = simple course, 1-4 = combined course, 99 = no info
         course_descr = cod_des_cur, # Description of course (TP secondary education only). 0: Does not apply, 1: Only High School, 2: Dual, 3: Other
         student_id = mrun,
         sex = gen_alu, # 0 = no info, 1 = male, 2 = female
         dob = fec_nac_alu_2, # The second one has DD
         age_june30 = edad_alu, # age at 30th June 2021
         special_needs_status = int_alu, # integrated student indicator, 0 = no, 1 = yes. Mostly no
         special_needs_code = cod_int_alu, # ADHD, blindness, etc. 0 = none. 105 = autism, 203 = ADHD. See ER_Matricula_por_alumno_PUBL_MRUN annex 7
         student_region_code = cod_reg_alu,
         student_commune_code = cod_com_alu,
         student_commune_name = nom_com_alu,
         economic_sector_code = cod_sec,
         economic_specialty_code = cod_espe,
         economic_branch_code = cod_rama,
         economic_profspec_code = cod_men,
         teaching_code_new = ens) %>%
  mutate(commune_code_temp = ifelse(student_commune_code == "0", school_commune_code, student_commune_code),
                             # If there is no commune code for the student, use their school's code instead
          commune_code_old = ifelse(nchar(as.character(commune_code_temp)) == 4,
                               paste0("0", as.character(commune_code_temp)),
                               as.character(commune_code_temp)),
         commune_code = ifelse(commune_code_old == "08401", "16101",
                        ifelse(commune_code_old == "08402", "16102",
                        ifelse(commune_code_old == "08403", "16202",
                        ifelse(commune_code_old == "08404", "16203",
                        ifelse(commune_code_old == "08405", "16302",
                        ifelse(commune_code_old == "08406", "16103",
                        ifelse(commune_code_old == "08407", "16104",
                        ifelse(commune_code_old == "08408", "16204",
                        ifelse(commune_code_old == "08409", "16303",
                        ifelse(commune_code_old == "08410", "16105",
                        ifelse(commune_code_old == "08411", "16106",
                        ifelse(commune_code_old == "08412", "16205",
                        ifelse(commune_code_old == "08413", "16107",
                        ifelse(commune_code_old == "08414", "16201",
                        ifelse(commune_code_old == "08415", "16206",
                        ifelse(commune_code_old == "08416", "16301",
                        ifelse(commune_code_old == "08417", "16304",
                        ifelse(commune_code_old == "08418", "16108",
                        ifelse(commune_code_old == "08419", "16305",
                        ifelse(commune_code_old == "08420", "16207",
                        ifelse(commune_code_old == "08421", "16109", commune_code_old))))))))))))))))))))))
```

```{r restructure data}
chile_bayes <- chile_merged %>%
  #select(-student_commune_name) %>%
  left_join(region_service_commune_lookup %>% as.tibble() %>% select(-geometry), by = "commune_code") %>%
  filter(age_june30 >= 6 & age_june30 <= 18,
         #special_needs_status == 1,
         sex != 0) %>%
  mutate(autism = ifelse(special_needs_code == 105, 1, 0),
         adhd = ifelse(special_needs_code == 203, 1, 0),
         age_cat_code = ifelse(age_june30 <= 8, 1, 
                   ifelse(age_june30 <= 11, 2, 
                   ifelse(age_june30 <= 14, 3, 4))),
         age_cat_name = ifelse(age_cat_code == 1, "6-8", 
                        ifelse(age_cat_code == 2, "9-11", 
                        ifelse(age_cat_code == 3, "12-14", "15-18"))),
          # 1 = 6-8, 2 = 9-11, 3 = 12-14, 4 = 15-18
         age_cat_name = factor(age_cat_name, levels = c("6-8", "9-11", "12-14", "15-18")),
         ethnic_2_group = ifelse(ethnic_3_group == "Other ethnic group", "Other Indigenous group",
                          ifelse(ethnic_3_group == "Aymara", "Other Indigenous group",
                          ifelse(ethnic_3_group == "No Native Group", "No Indigenous group", ethnic_3_group))),
         school_rurality = ifelse(school_rurality_code == 0, "Urban", "Rural"),
         school_fee_temp = school_fee,
         school_fee = ifelse(school_fee == "", "No information", 
                      ifelse(school_fee == "GRATUITO", "Free", 
                      ifelse(school_fee == "$1.000 A $10.000", "$1,000-$10,000",
                      ifelse(school_fee == "$10.001 A $25.000", "$10,001-$25,000", 
                      ifelse(school_fee == "$25.001 A $50.000", "$25,001-$50,000",
                      ifelse(school_fee == "$50.001 A $100.000", "$50,001-$100,000", 
                      ifelse(school_fee == "MAS DE $100.000", "$100,001+", 
                      ifelse(school_fee == "SIN INFORMACION", "No information", NA)))))))),
         school_fee = factor(school_fee, levels = c("Free", "$1,000-$10,000", 
                                                    "$10,001-$25,000", "$25,001-$50,000",
                                                    "$50,001-$100,000", "$100,001+", 
                                                    "No information")),
         school_fee_group = ifelse(school_fee == "Free", "Free", 
                            ifelse(school_fee %in% c("$1,000-$10,000", "$10,001-$25,000",
                                                     "$25,001-$50,000", "$50,001-$100,000"), "Low",
                            ifelse(school_fee == "$100,001+", "Medium", 
                            ifelse(school_fee == "No information", "No information", NA)))),
         school_fee_group = factor(school_fee_group, levels = c("Free", "Low", "Medium",
                                                                "No information"))) %>% 
  select(#school_region_name_abr,
    region_code,
    region_name,
    region_name_abr,
    commune_code, # student, see chile_merged
    student_commune_name, # upper case, from chile_merged
    commune_name, # Sentence case, from lookup table
    health_service_code,
    health_service_name,
    sex,
    sex_desc,
    age_june30,
    age_cat_code,
    age_cat_name,
    school_rurality_code,
    school_rurality,
    pago_matricula,
    pago_mensual,
    school_fee,
    school_fee_group,
    school_fee_temp,
    ethnicity,
    mapuche,
    nationality,
    ethnic_3_group,
    ethnic_2_group,
    autism,
    adhd
  ) 

chile_bayes_aut <- chile_bayes %>% select(-adhd)
chile_bayes_adhd <- chile_bayes %>% select(-autism)
```

```{r import clinical data}
clinical_large_raw <- read_excel("04_Data/dataset_ssas_2015_2021.xlsx") %>% clean_names
#describe(clinical_raw)

clinical_large <- clinical_large_raw %>%
  select(c(-procedence, -ethnicity, -education_level, -disability, -foster_care)) %>%
  # Fix the date columns
  mutate(dob_eng = ifelse(str_detect(date_of_birth, "/"), 1,
                   ifelse(str_detect(date_of_birth, "-"), 0, NA)),
         apt_eng = ifelse(str_detect(date_appointment, "/"), 1, ifelse(str_detect(date_appointment, "-"), 0, NA)),
         dob_day = ifelse(dob_eng == 1, as.integer(str_extract(date_of_birth, "^\\d+")), 
                   ifelse(dob_eng == 0, as.integer(str_extract(date_of_birth, "^\\d+")), NA)),
         dob_month = ifelse(dob_eng == 1, as.integer(str_extract(date_of_birth, "(?<=/)\\d+(?=/)")), 
                     ifelse(dob_eng == 0, str_extract(date_of_birth, "(?<=-)\\w+(?=-)"), NA)),
         dob_year = ifelse(dob_eng == 1, as.integer(str_extract(date_of_birth, "\\d+$")), 
                    ifelse(dob_eng == 0, as.integer(str_extract(date_of_birth, "\\d+$")) + 2000, NA)),
         dob_month_eng = as.integer(ifelse(dob_month == "ene", 1,
                                    ifelse(dob_month == "abr", 4, 
                                    ifelse(dob_month == "ago", 8, 
                                    ifelse(dob_month == "sept", 9, 
                                    ifelse(dob_month == "dic", 12, dob_month)))))),
         dob = make_date(year = dob_year, month = dob_month_eng, day = dob_day),
         apt_day = ifelse(apt_eng == 1, as.integer(str_extract(date_appointment, "^\\d+")), 
                   ifelse(apt_eng == 0, as.integer(str_extract(date_appointment, "^\\d+")), NA)),
         apt_month = ifelse(apt_eng == 1, as.integer(str_extract(date_appointment, "(?<=/)\\d+(?=/)")), 
                     ifelse(apt_eng == 0, str_extract(date_appointment, "(?<=-)\\w+(?=-)"), NA)),
         apt_year = ifelse(apt_eng == 1, as.integer(str_extract(date_appointment, "\\d+$")), 
                    ifelse(apt_eng == 0, as.integer(str_extract(date_appointment, "\\d+$")) + 2000, NA)),
         apt_month_eng = as.integer(ifelse(apt_month == "ene", 1,
                                    ifelse(apt_month == "abr", 4, 
                                    ifelse(apt_month == "ago", 8, 
                                    ifelse(apt_month == "sept", 9, 
                                    ifelse(apt_month == "dic", 12, apt_month)))))),
         apt_date = make_date(year = apt_year, month = apt_month_eng, day = apt_day),
         age_june30 = trunc(time_length(interval(ymd(dob), ymd("2021-06-30")), unit = "year")),
         commune_name_upper = ifelse(comuna == "CHOL CHOL", "CHOLCHOL",
                        ifelse(comuna == "CURACAUTIN", "CURACAUTÍN",
                        ifelse(comuna == "PITRUFQUEN", "PITRUFQUÉN",
                        ifelse(comuna == "PUCON", "PUCÓN",
                        ifelse(comuna == "TOLTEN", "TOLTÉN",
                        ifelse(comuna == "VILCUN", "VILCÚN", comuna)))))),
         #commune_name_upper = comuna,
         ses_status = ifelse(socio_economic_level == "FONASA - A", 1, 
                      ifelse(socio_economic_level == "FONASA - B", 2,
                      ifelse(socio_economic_level == "FONASA - C", 2, 
                      ifelse(socio_economic_level == "FONASA - D", 2,
                      ifelse(socio_economic_level == "Private Health Insurance", 3, 
                      ifelse(socio_economic_level %in% c("COLMENA GOLDEN CROSS", "RIO BLANCO", "CARABINEROS (DIPRECA)", "BANMEDICA S.A.", "PARTICULAR (SIN PREVISION)", "VIDA TRES"), 3, NA)))))),
         autism = 1,
         intdisab = 0,
         aut_rank = 1
         ) %>%
  left_join(region_service_commune_lookup, by = "commune_name_upper") %>%
  select(id, gender, 
         commune_code, commune_name, commune_name_upper, 
         health_service_name, region_name, 
         socio_economic_level, ses_status, 
         dob, age_june30, 
         apt_date, hospital, medical_specialty, type_appointment,
         autism, intdisab, aut_rank) 

aut_codes <- unique(clinical_large_raw$codigo)

clinical_small_raw <- read_excel("04_Data/Dataset_Vill_2014_2021.xlsx", col_names = TRUE) %>% clean_names()

clinical_small <- clinical_small_raw %>%
  rename("dob" = "fecha_nacimiento",
         "apt_date" = "fecha_ejecutada",
         "type_appointment" = "appoinment",
         "diagnosis" = "diagnostico_1") %>%
  mutate(gender = str_to_title(gender),
         autism = ifelse(cod_dg_1 %in% aut_codes | 
                           cod_dg_2 %in% aut_codes | 
                           cod_dg_3 %in% aut_codes, 1, 0),
         aut_rank = ifelse(cod_dg_1 %in% aut_codes, 1,
                    ifelse(cod_dg_2 %in% aut_codes, 2,
                    ifelse(cod_dg_3 %in% aut_codes, 3, NA))),
         age_june30 = trunc(time_length(interval(ymd(dob), ymd("2021-06-30")), unit = "year")),
         commune_name_upper = ifelse(comuna == "CHOL CHOL", "CHOLCHOL",
                        ifelse(comuna == "CURACAUTIN", "CURACAUTÍN", 
                        ifelse(comuna == "PITRUFQUEN", "PITRUFQUÉN", 
                        ifelse(comuna == "PUCON", "PUCÓN", 
                        ifelse(comuna == "TOLTEN", "TOLTÉN", 
                        ifelse(comuna == "VILCUN", "VILCÚN", 
                        ifelse(comuna == "DIEGO DE ALMAGRO  (#)", "DIEGO DE ALMAGRO",
                        ifelse(comuna == "MACHALI", "MACHALÍ",
                        ifelse(comuna == "TEMUCO (##)", "TEMUCO", comuna))))))))),
         ses_status = ifelse(socio_economic_level == "FONASA - A", 1, 
                      ifelse(socio_economic_level == "FONASA - B", 2,
                      ifelse(socio_economic_level == "FONASA - C", 2, 
                      ifelse(socio_economic_level == "FONASA - D", 2,
                      ifelse(socio_economic_level == "Private Health Insurance", 3, 
                      ifelse(socio_economic_level %in% c("COLMENA GOLDEN CROSS", "RIO BLANCO", "CARABINEROS (DIPRECA)", "BANMEDICA S.A.", "PARTICULAR (SIN PREVISION)", "VIDA TRES"), 3, NA))))))
         ) %>%
  left_join(region_service_commune_lookup, by = "commune_name_upper") %>%
  #filter(autism == 1) %>%
  select(id, gender, commune_code, commune_name, commune_name_upper, health_service_name, region_name, socio_economic_level, ses_status, dob, age_june30, apt_date, hospital, medical_specialty, type_appointment, cod_dg_1, cod_dg_2, cod_dg_3, diagnosis, autism, aut_rank) 
# Throws a warning because there are 2 records for Tocopila which is in two regions. Will keep both because we have no way of knowing which is correct.
# Doesn't anymore because I changed the lookup to have only 1 Tocopilla row

intdisab_codes <- unique(c(clinical_small_raw$cod_dg_1, clinical_small_raw$cod_dg_2, clinical_small_raw$cod_dg_3)) %>%
  str_subset("F7") %>%
  sort() 

clinical_small <- clinical_small %>% 
  mutate(intdisab = ifelse(cod_dg_1 %in% intdisab_codes |
                             cod_dg_2 %in% intdisab_codes | 
                             cod_dg_3 %in% intdisab_codes, 1, 0)) %>%
  #rename("codigo" = "cod_dg_1") %>%
  select(c(-cod_dg_1, -cod_dg_2, -cod_dg_3, -diagnosis))

clinical <- rbind(clinical_large, clinical_small)

clinical_communes <- clinical %>% group_by(commune_code) %>% summarise() %>% arrange() %>%
  mutate(commune_in_school_data = ifelse(commune_code %in% unique(chile_merged$commune_code), 1, 0)) # Needs to all be 1's

```


```{r functions bayes}

get_grouped_prev_plot <- function(x, grouping_vars, disease) {
  # Calculates sample prevalence and its confidence intervals for supplied feature grouping
  # x = chile_bayes_aut or chile_bayes_adhd, needs columns called autism or adhd, and count
  # grouping_vars = variables in x to group by
  # disease = autism or adhd
  
  x_grouped <- x %>% 
    group_by(across(all_of(grouping_vars))) %>%
    summarise(count = n()) %>%
    pivot_wider(names_from = disease, values_from = count) %>%
    rename("n_nodisease" = "0", "n_disease" = "1") %>% #, "age" = "age_june30") %>%
    mutate(n_disease = ifelse(is.na(n_disease), 0, n_disease), # If there are no cases of autism in the group, input 0
           sample_pop_size = n_nodisease + n_disease, # Total sample population is autism cases + not cases
           sample_prevalence = n_disease / sample_pop_size, # Prevalence of autism in the group
           ci_lower = sample_prevalence - (1.96 * sqrt(sample_prevalence * (1 - sample_prevalence) / sample_pop_size)),
           ci_upper = sample_prevalence + (1.96 * sqrt(sample_prevalence * (1 - sample_prevalence) / sample_pop_size))) %>%
    ungroup()
  return(x_grouped)
}

get_grouped_prev <- function(x, stdpop, grouping_vars, disease) {
  # Calculates sample prevalence, age- and sex-standardised prevalence and group weighting for supplied feature grouping
  # x = chile_bayes_aut, needs columns called autism, count
  # stdpop = standard population with age and sex counts
  # grouping_vars = variables in x to group by
  # disease = autism or adhd
  
  n_stdpop <- sum(stdpop$std_pop)
  
  x_grouped <- x %>% 
    group_by(across(all_of(grouping_vars))) %>%
    summarise(count = n()) %>%
    pivot_wider(names_from = disease, values_from = count) %>%
    rename("n_nodisease" = "0", "n_disease" = "1", "age" = "age_june30") %>%
    mutate(n_disease = ifelse(is.na(n_disease), 0, n_disease), # If there are no cases of autism in the group, input 0
           sample_pop_size = n_nodisease + n_disease, # Total sample population is autism cases + not cases
           sample_prevalence = n_disease / sample_pop_size) %>% # Prevalence of autism in the group
    left_join(stdpop, by = c("age", "sex")) %>%
    mutate(disease_prev_std = n_disease / sample_pop_size * pop_prop, # Prevalence of autism in the group, standardised to standard population
           w = std_pop / (sample_pop_size * n_stdpop), # Weight of the group using standard population
           w2 = pop_prop / sample_pop_size,
           #sum_std_pop = sum(std_pop)
           ) %>%
    ungroup()
  return(x_grouped)
}

get_adjusted_prev <- function(x, grouping_vars) {
  # Turns grouped prevalences into age- and sex- adjusted prevalences with Fay and Feuer Gamma confidence intervals
  # x = output from get_grouped_prev
  x_adj <- x %>%
  group_by(across(all_of(grouping_vars))) %>%
  summarise(sum_sample_pop_size = sum(sample_pop_size),
            crude_rate = sum(n_disease) / sum(sample_pop_size),
            crude_count = sum(n_disease),
            adjusted_rate = sum(n_disease / sample_pop_size * pop_prop),
            adjusted_count = round(adjusted_rate * sum_sample_pop_size, 0), # had to fudge this to get MCMC to run bc it needs integers
            #adjusted_count = adjusted_rate * sum_sample_pop_size,
            var = sum(pop_prop^2 * n_disease / sample_pop_size^2),
            #se2 = sqrt(sum((std_pop/sum(std_pop))^2 * n_autism/sample_pop_size^2)),
            w_M = max(w),
            crude_ci_lower = crude_rate - (1.96 * sqrt(crude_rate * (1 - crude_rate) / sum_sample_pop_size)),
            crude_ci_upper = crude_rate + (1.96 * sqrt(crude_rate * (1 - crude_rate) / sum_sample_pop_size)),
            adjusted_ci_lower = ifelse(var == 0, 0, var / (2*adjusted_rate) * qchisq(p = 0.05/2, df = 2*adjusted_rate^2 / var)),
            adjusted_ci_upper = (var + w_M^2) / (2*(adjusted_rate + w_M)) * qchisq(p = 1-0.05/2, df = 2*(adjusted_rate+w_M)^2 / (var+w_M^2))) %>%
  arrange(across(all_of(grouping_vars)))
}

do_jags_rand_model <- function(x, feat, model, theta_mu, theta_sigma, pars, nBurn = 1000, nIter = 1000, convergence_checks = FALSE) {
  # x = output from get_adjusted_prev. Needs to have columns sum_sample_pop_size, adjusted_count
  # feat = feature being used as random effect
  # model = JAGS random effects model
  # theta_mu, theta_sigma = mean and sd of beta prior distribution
  # pars = model parameters to report
  # nBurn = number of burn-in samples
  # nIter = number of posterior iterations
  
  nFeat <- length(unique(x[[feat]]))
  FeatNames <- sort(unique(x[[feat]]))
  
  # Define beta prior
  theta_a <- theta_mu * (theta_mu * (1-theta_mu) / theta_sigma^2 - 1)
  theta_b <- (1 - theta_mu) * (theta_mu * (1-theta_mu) / theta_sigma^2 - 1)
  
  # Initial values for model chains
  rand_ini <- list(list(theta = rep(0.001, nFeat)), #, spec = 0.5, sens = 0.5),
                   list(theta = rep(0.01, nFeat))) #, spec = 0.9, sens = 0.9)) 
  
  # Run JAGS model
  rand_data <- list(theta_a = theta_a, 
                    theta_b = theta_b,
                    nObs = x$sum_sample_pop_size,
                    disease_sample = x$adjusted_count,
                    nFeat = nFeat)
  rand_jag <- jags.model(textConnection(model),
                         data = rand_data,
                         inits = rand_ini,
                         n.chains = 2,
                         quiet = TRUE)
  update(rand_jag, n.iter = nBurn)
  rand_sam <- coda.samples(model = rand_jag,
                           variable.names = pars,
                           n.iter = nIter)
  
  # Convergence checks
  if(convergence_checks) {
    print(mcmc_trace(rand_sam, paste0("theta[", 1:nFeat, "]"))) # Convergence looks fine and rhats <= 1.1
    print(mcmc_trace(rand_sam, paste0("disease_pred[", 1:nFeat, "]"))) # Convergence looks fine and rhats <= 1.1
    rand_summ <- summary(subset_draws(as_draws(rand_sam), pars),
                         ~quantile(.x, probs=c(0.025, 0.5, 0.975)),
                         ~mcse_quantile(.x, probs=c(0.025, 0.5, 0.975)),
                         "rhat") %>%
      arrange(desc(rhat))
    print(rand_summ)
  }
  
  # Extract posterior density
  prev_post <- as_tibble(as_draws_matrix(rand_sam), rownames = "Iteration") %>%
    select(c("Iteration", contains("theta["))) %>%
    pivot_longer(cols = contains("theta["),
                 names_to = "Feat",
                 values_to = "predicted_prev") %>%
    mutate(Feat_names = factor(Feat, levels = c(paste0("theta[",1:nFeat,"]")), labels = FeatNames)) %>%
    select(Iteration, Feat_names, predicted_prev)
  
  return(prev_post)
}


plot_post_density <- function(jags_post, sample_data, feat, theta_mu, theta_sigma, disease, title_text = "") {
  # Plots posterior densities and their 95% credible intervals, and sample prevalence confidence intervals
  # jags_post = output from do_jags_rand_model, ie posterior densities
  # sample data = output from get_adjusted_prev, ie sample prevalences with confidence intervals
  # feat = the same feature used as the random effect in do_jags_rand_model
  # theta_mu, theta_sigma = mean and sd of beta prior distribution used in do_jags_rand_model
  # disease = autism or ADHD
  # title_text = any additional text for the title, eg grouing variables
  
  # calcuate posterior credible intervals
  post_ci <- jags_post %>%
  group_by(across(all_of(feat))) %>%
  summarise(post_lower = quantile(predicted_prev, 0.025),
            post_upper = quantile(predicted_prev, 0.975))
  
  print(ggplot() +
          geom_density(data = jags_post, aes(x = predicted_prev)) +
          geom_vline(data = post_ci, aes(xintercept = post_lower), color = "blue", linetype = "dotted") +
          geom_vline(data = post_ci, aes(xintercept = post_upper), color = "blue", linetype = "dotted") +
          geom_vline(data = sample_data, aes(xintercept = adjusted_ci_lower), color = "red", linetype = "dashed") +
          geom_vline(data = sample_data, aes(xintercept = adjusted_ci_upper), color = "red", linetype = "dashed") +
          facet_wrap(as.formula(paste0("~", feat))) +
          labs(title = paste0(disease, " prevalence, prior mean = ", signif(theta_mu, 3), ", prior sd = ", signif(theta_sigma, 3), title_text),
               x = "Posterior predictive distribution",
               y = "Density"))
}


```

```{r functions restructure}
# Define some functions to help with restructuring clinical data into patient level data
get.min.na <- function(x) ifelse( !all(is.na(x)), min(x, na.rm = TRUE), NA)

get.max.na <- function(x) ifelse( !all(is.na(x)), max(x, na.rm = TRUE), NA)

get.mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

get.yes.disability <- function(x) {
  y <- NA
  if(any(x == "Yes")) {
    y <- "Yes disability"
  } else if(any(x == "No")) {
    y <- "No disability"
  } else {
    y <- "No disability information"
  }
  return(y)
}

get.yes.fostercare <- function(x) {
  y <- NA
  if(any(x == "Yes")) {
    y <- "Yes foster care"
  } else if(any(x == "No")) {
    y <- "No foster care"
  } else {
    y <- "No foster care information"
  }
  return(y)
}


```



# Abstract

TODO


# Declaration

This dissertation is the result of my own work and includes nothing which is the outcome of work done in collaboration except where specifically indicated in the text.

USN: xxxxx July, 2022

TODO - is this section needed?


# Introduction

TODO - copy in intro text

```{r map}
#commune_geoms <- data.frame(mapa_comunas)
#communes_lookup <- data.frame(codigos_territoriales)

# Get region-level geometries with demographic data for plotting
demog_geom <- chile.adm1 %>%
  left_join(region_lookup, by = "ADM1_PCODE") %>%
  left_join(chile_regionpop, by = "region_name") %>%
  left_join(chile_regionincome, by = "region_name")

#chile.adm2 <- st_read("04_Data/CHL_adm/CHL_adm2.shp") # Also doesn't have Biobio
#chile.adm2 <- st_transform(chile.adm2, crs = 32629)

#region_geoms_demog <- region_geoms %>%
#  left_join(chile_regionpop, by = "nombre_region") %>%
#  left_join(chile_regionincome, by = "nombre_region") %>%
#  select(-region)
```

```{r map pop, include = TRUE, fig.cap = "Population of 0-14 year olds in Chile in 2021 by region, from 2017 census projections."}
# Population
ggplot(demog_geom) + 
  geom_sf(mapping = aes(geometry = geometry, fill = youth_pop_2021), linewidth = 0.01) +
  geom_sf_text(mapping = aes(geometry = geometry, label = region_name), nudge_x = 8, size = 3) +
  scale_fill_viridis(option = "viridis", direction = 1, name = "Population") + #, limits = c(23000, 400000), oob = scales::squish) +
  labs(title = "Population aged 0-14 (2021 projections)") +
  xlab("Longitude") +
  ylab("Latitude") +
  coord_sf(xlim = c(-85, -50), ylim = c(-60, -15))
```

```{r map income, include = TRUE, fig.cap = "Net income from main job in Chile in 2021 by region, from the INE's Supplementary Income Survey."}
# Income
ggplot(demog_geom) + 
  geom_sf(mapping = aes(geometry = geometry, fill = ingreso_medio_nominal), linewidth = 0.01) +
  geom_sf_text(mapping = aes(geometry = geometry, label = region_name), nudge_x = 8, size = 3) +
  scale_fill_viridis(option = "viridis", direction = 1, name = "Median income (Peso)") +
  labs(title = "Net income (2021)") +
  xlab("Longitude") +
  ylab("Latitude") +
  coord_sf(xlim = c(-85, -50), ylim = c(-60, -15))
```


```{r health to region, fig.cap = "Residential communes aggregated to region level and the health services associated with the aggregated communes, with counts of the number of students resident in the communes in each health service's catchment area."}
map_tab_df <- as.data.frame(table(chile_bayes$region_name, chile_bayes$health_service_name))
ggplot(map_tab_df, aes(x = Var1, y = Var2, fill = Freq)) +
  geom_tile() +
  scale_fill_viridis_c(option = "rocket", direction = -1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  scale_y_discrete(limits = rev(levels(map_tab_df$Var2))) +
  labs(title = "Students' residential region and health service",
       x = "Region", y = "Health service", fill = "Count")

```

```{r map health services, include = FALSE, fig.cap = "Health services in Chile, coloured by region they serve."}
# Income

# health_service_geom <- region_service_commune_lookup %>%
#   group_by(health_service_name) %>% 
#   summarize(geometry = st_union(geometry))
# 
# ggplot(region_service_commune_lookup %>% filter(health_service_name == "Iquique")) + 
#   geom_sf(mapping = aes(geometry = geometry, fill = health_service_name), linewidth = 0.01) +
#   geom_sf_text(mapping = aes(geometry = geometry, label = commune_name), nudge_x = 8, size = 3) +
#   #scale_fill_viridis(option = "viridis", direction = 1, name = "Health service") +
#   labs(title = "Net income (2021)") +
#   xlab("Longitude") +
#   ylab("Latitude") #+
#   #coord_sf(xlim = c(-85, -50), ylim = c(-60, -15))
# 
# 
# region_service_commune_lookup %>% 
#   filter(health_service_name == "Iquique") %>%
#   summarise(geometry = st_union(geometry))
```

```{r map arauc, fig.cap = "Communes in the Araucanía region, coloured red for the Araucanía Norte (north Araucanía) health services and blue for the Araucanía Sur (south Araucanía) health service."}
# ARAUC communes
arauc <- region_service_commune_lookup %>%
  filter(ADM1_PCODE == "CL09")

ggplot(arauc) +
  geom_sf(mapping = aes(geometry = geometry, fill = health_service_name)) +
  geom_sf_text(mapping = aes(geometry = geometry, label = commune_name), size = 3) +
  coord_sf(xlim = c(-74, -70.5), ylim = c(-40, -37.5)) +
  labs(title = "Communes in La Araucania") +
  xlab("Longitude") +
  ylab("Latitude")
```

# Methods

TODO - copy in methods


# Results

TODO - text explaining figures
TODO - table formatting

## School data

TODO - table summarising data content

In the school data, `r chile_merged %>% filter(student_commune_code == "0") %>% nrow` (`r round(chile_merged %>% filter(student_commune_code == "0") %>% nrow / nrow(chile_merged) * 100, 2)`%) students were missing commune of residence. These missing values were imputed with their school's commune as most students are likely to go to school near their place of residence.

## Clinical data

TODO - table summarising data content. Number of unique patients

## Probabilistic data linkage

```{r patients}
patients <- clinical %>%
  filter(commune_code %in% araucsur_communes$commune_code) %>%
  group_by(id, gender, dob, commune_name, region_name) %>%
  summarise(ses_status = get.min.na(ses_status),
            autism = get.max.na(autism),
            aut_rank = get.min.na(aut_rank)) %>%
  ungroup() %>% 
  rename("student_commune_name" = "commune_name",
         "student_region_name" = "region_name",
         "sex_desc" = "gender") %>%
  rowid_to_column("row_id") %>%
  select(row_id, 
         id,
         dob, 
         sex_desc,
         student_commune_name,
         autism,
         ses_status,
         #intdisab,
         aut_rank) #, student_region_name) 

```

NB: there are 1688 unique ID's in patients and it's 1702 rows long because some people are represented in 2 communes.

```{r school}
school <- chile_merged %>%
  select(-student_commune_name) %>%
  left_join(region_service_commune_lookup %>% as.tibble %>% select(-geometry), by = "commune_code") %>%
  filter(commune_code %in% araucsur_communes$commune_code) %>%
  filter(age_june30 >= 6 & age_june30 <= 18, sex != 0) %>% 
  mutate(autism = ifelse(special_needs_code == 105, 1, 0),
         aut_rank = 1,
         dob = ymd(dob),
         ses_status = ifelse(school_fee == "", NA, 
                      ifelse(school_fee == "GRATUITO", 1, 
                      ifelse(school_fee == "$1.000 A $10.000", 2,
                      ifelse(school_fee == "$10.001 A $25.000", 2, 
                      ifelse(school_fee == "$25.001 A $50.000", 2,
                      ifelse(school_fee == "$50.001 A $100.000", 2, 
                      ifelse(school_fee == "MAS DE $100.000", 2, 
                      ifelse(school_fee == "SIN INFORMACION", NA, NA))))))))) %>%
  filter(autism == 1) %>%
    # We only want to find additional autism cases in the clinical records, we don't care if a student has autism and isn't in the clinical records
  rename(student_commune_name = commune_name) %>%
  select(dob,
         sex_desc,
         student_commune_name,
         #commune_name, 
         #health_service_name,
         autism,
         ses_status,
         #intdisab,
         aut_rank#,
         #student_region_name
  ) %>%
  rowid_to_column("id")

# Add a fake row so that pairing works later
school[dim(school)[1]+1, ] <- c(dim(school)[1]+1, "2023-06-26", "Female", "Misc", 0, 3, 0)
```

### Number matched

```{r manual linkage}
patients_grouped <- patients %>%
  group_by(sex_desc, 
           dob, 
           student_commune_name) %>%
  summarise(count = n(),
            ids = list(id))

school_grouped <- school %>%
  group_by(sex_desc, 
           dob, 
           student_commune_name) %>%
  summarise(count = n(),
            #ids = list(rowid)
            ses = list(ses_status))

merged <- merge(school, patients, by = c("sex_desc", "dob", "student_commune_name"), all = FALSE)
#merged %>% filter(!is.na(id.x) & !is.na(id.y)) # 205 matches


```

Using perfect match on sex, date of birth and commune of residence, `r nrow(merged)` matches can be found between the school and patient records.
`r length(unique(merged$id.x)) - 1` unique school records can be perfectly matched to clinical records. `r length(unique(merged$id.y))` patients can be linked to school records.

```{r probabilistic weights}
# formerly a2
pairs_blocked <- compare.linkage(school,
                     select(patients, -row_id),
                     blockfld = c("sex_desc", "dob"), 
                      # Block on sex and dob because we really want them to be the same and helps computation time
                     phonetic = FALSE,
                     strcmp = c(2), # Do string comparison on DOB
                     exclude = c(1) # Exclude the id column in both datasets
                     )

pairs_weighted <- epiWeights(pairs_blocked, e = c(0.01, # Default for DOB
                           0.01, # Default for sex
                           0.01, # Default for commune because we want a good match
                           0.01, # Keep small so autism in clinical (not intellectual disability) is prioritised over ses match
                           0.4, # Have more error for ses_status because it is loosely defined 
                           0.01)) # Allow some mismatch on whether autism is the primary diagnosis 
                                  # so we take record with higher placed autism diagnosis when there 
                                  # are multiple clinical record options for a single school record

#summary(pairs_weighted)
#allPairs2 <- getPairs(pairs_weighted)
#head(allPairs2, n = 20)

pairs_classified <- emClassify(pairs_weighted, threshold.upper = 1, threshold.lower = 0.8)

pairs_blocked.df <- pairs_blocked$pairs %>%
  mutate(weight = pairs_classified$Wdata,
         pred = pairs_classified$prediction) %>%
  rename(".x" = id1, ".y" = id2) %>%
  select(-is_match)

#finalPairs2 <- getPairs(b2, max.weight = 1, min.weight = 0, single.rows = TRUE) # Take them all when blocked on sex_desc and dob together

# Turn into a 'pairs' type object so it can be fed to select_n_to_m()
pairs_blocked.pairs <- pair_blocking(school, patients, on = c("sex_desc", "dob")) %>%
         mutate(student_commune_name = (school$student_commune_name[.x] == patients$student_commune_name[.y])#,
         #ses = get_num_diff(school$ses_status[.x], patients$ses_status[.y])$val
         ) %>%
  left_join(pairs_blocked.df, by = c(".x", ".y")) %>%
  select(c(-student_commune_name.x)) %>%
  rename("student_commune_name" = "student_commune_name.y")

matches <- select_n_to_m(pairs_blocked.pairs, threshold = 0.5, score = "weight", n = 1, m = 1, var = "match") %>%
  filter(match == TRUE) %>%
  rename("id" = ".x",
         "row_id" = ".y") %>%
  mutate(id = as.character(id))
```


```{r match school}

# Now add the matched clinical records to the school records
school_matched <- school %>%
  filter(student_commune_name != "Misc") %>%
  left_join(matches, by = "id") %>%
  rename(id.school = id,
         dob.school = dob.x,
         sex_desc.school = sex_desc.x,
         student_commune_name.school = student_commune_name.x,
         ses_status.school = ses_status.x,
         dob.matched = dob.y,
         sex_desc.matched = sex_desc.y,
         student_commune_name.matched = student_commune_name.y,
         ses_status.matched = ses_status.y) %>%
  select(c(-pred, -match)) %>%
  left_join(patients, by = "row_id") %>%
  rename(id.patient = row_id,
         patient_id = id,
         dob.patient = dob,
         sex_desc.patient = sex_desc,
         student_commune_name.patient = student_commune_name,
         ses_status.patient = ses_status) %>%
  select(id.school, id.patient, patient_id,
         dob.school, dob.patient, dob.matched,
         sex_desc.school, sex_desc.patient, sex_desc.matched,
         student_commune_name.school, student_commune_name.patient, student_commune_name.matched,
         ses_status.school, ses_status.patient, ses_status.matched,
         weight) %>%
  arrange(desc(weight))

school_matched_small <- school_matched %>%
  mutate(matched = ifelse(is.na(patient_id), 0, 1),
         sex.school = ifelse(sex_desc.school == "Male", 1,
                      ifelse(sex_desc.school == "Female", 2, NA))) %>%
  merge(region_service_commune_lookup %>% as.tibble() %>% select(-geometry),
        by.x = "student_commune_name.school", by.y = "commune_name") %>% # doesn't include all.x = TRUE because that would keep the fake record.
  select(id.school, 
         dob.school, 
         sex_desc.school, sex.school,
         student_commune_name.school, commune_code,
         ses_status.school, 
         matched)

```

```{r match patient}

# Now add the matched clinical records to the school records
patients_matched <- patients %>%
  left_join(matches, by = "row_id") %>%
  rename(id.patient = row_id,
         patient_id = id.x,
         dob.patient = dob.x,
         sex_desc.patient = sex_desc.x,
         student_commune_name.patient = student_commune_name.x,
         id = id.y,
         ses_status.patient = ses_status.x,
         dob.matched = dob.y,
         sex_desc.matched = sex_desc.y,
         student_commune_name.matched = student_commune_name.y,
         ses_status.matched = ses_status.y) %>%
  select(c(-pred, -match)) %>%
  left_join(school, by = "id") %>%
  rename(id.school = id,
         dob.school = dob,
         sex_desc.school = sex_desc,
         student_commune_name.school = student_commune_name,
         ses_status.school = ses_status) %>%
  select(id.school, id.patient, patient_id,
         dob.school, dob.patient, dob.matched,
         sex_desc.school, sex_desc.patient, sex_desc.matched,
         student_commune_name.school, student_commune_name.patient, student_commune_name.matched,
         ses_status.school, ses_status.patient, ses_status.matched,
         weight) %>%
  arrange(desc(weight))

patients_matched_small <- patients_matched %>%
  mutate(matched = ifelse(is.na(id.school), 0, 1),
         sex.patient = ifelse(sex_desc.patient == "Male", 1,
                       ifelse(sex_desc.patient == "Female", 2, NA))) %>%
  merge(region_service_commune_lookup %>% as.tibble() %>% select(-geometry),
        by.x = "student_commune_name.patient", by.y = "commune_name") %>%
  select(patient_id, id.patient, 
         dob.patient,
         sex_desc.patient, sex.patient,
         student_commune_name.patient, commune_code,
         ses_status.patient,
         matched)

```


```{r patients unique}
patients_matched_unique <- patients_matched_small %>%
  group_by(matched, patient_id) %>%
  summarise(count = n())

patients_dup <- patients_matched_unique %>% filter(matched == 1, count > 1) %>% select(patient_id)
# No patient is inadvertently matched to two school records

```

There are no patients that lived in different communes therefore were in the patient dataset twice that are matched to multiple school records.

### Differences between un/matched


```{r kolmogorov tests school, warning = FALSE}

school_yes <- school_matched_small %>% filter(matched == 1) #%>% select(sex.school)
school_no <- school_matched_small %>% filter(matched == 0)

# Kolmogorov tests for our matched results
ks.school.sex <- ks.test(na.omit(school_yes$sex.school),
                         na.omit(school_no$sex.school),
                         alternative = "two.sided", simulate.p.value = TRUE)
ks.school.sex

ks.school.ses_status <- ks.test(as.numeric(na.omit(school_yes$ses_status.school)),
                                as.numeric(na.omit(school_no$ses_status.school)),
                                alternative = "two.sided", simulate.p.value = TRUE)
ks.school.ses_status

ks.school.commune_code<- ks.test(as.numeric(na.omit(school_yes$commune_code)),
                                 as.numeric(na.omit(school_no$commune_code)),
                                 alternative = "two.sided", simulate.p.value = TRUE)
ks.school.commune_code

# Kolmogorov tests with permutation distributions
set.seed(123)
nPerm <- 200 # change to 2000
ks_perm.school.pvals <- data.frame(sex = numeric(nPerm),
                                   commune_code = numeric(nPerm),
                                   ses_status = numeric(nPerm))

school_matched_small_perm <- school_matched_small

for (i in 1:nPerm) {
  #print(i)
  school_matched_small_perm$matched <- school_matched_small$matched[sample(nrow(school_matched_small))] # permute matched status
  school_perm_yes <- school_matched_small_perm %>% filter(matched == 1)
  school_perm_no <- school_matched_small_perm %>% filter(matched == 0)
  
  ks_perm.school.sex <- ks.test(na.omit(school_perm_yes$sex.school),
                                na.omit(school_perm_no$sex.school), 
                                alternative = "two.sided")
  ks_perm.school.commune_code <- ks.test(as.numeric(na.omit(school_perm_yes$commune_code)),
                                        as.numeric(na.omit(school_perm_no$commune_code)),
                                        alternative = "two.sided")
  ks_perm.school.ses_status <- ks.test(as.numeric(na.omit(school_perm_yes$ses_status.school)),
                                       as.numeric(na.omit(school_perm_no$ses_status.school)),
                                       alternative = "two.sided")
  
  ks_perm.school.pvals$sex[i] <- ks_perm.school.sex$p.value
  ks_perm.school.pvals$commune_code[i] <- ks_perm.school.commune_code$p.value
  ks_perm.school.pvals$ses_status[i] <- ks_perm.school.ses_status$p.value
}

# Results for sex
school_match_yes.sex <- school_yes %>% group_by(sex.school) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 1)
school_match_no.sex <- school_no %>% group_by(sex.school) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 0)
school_match.sex <- rbind(school_match_yes.sex, school_match_no.sex) %>%
  mutate(sex_desc = ifelse(sex.school == 1, "Male", ifelse(sex.school == 2, "Female", NA))) %>% 
  arrange(sex_desc, matched)

ggplot(school_match.sex) +
  geom_col(aes(x = as.factor(matched), y = freq, fill = as.factor(matched))) +
  facet_wrap(~sex_desc) +
  labs(title = "Matching of school record to clinical record by sex",
       x = "Matched status",
       y = "Feature frequency",
       fill = "Matched status")

ggplot(ks_perm.school.pvals, aes(x = sex, y = after_stat(density))) +
  geom_density() +
  geom_vline(xintercept = ks.school.sex$p.value, color = "red")

# Results for commune
school_match_yes.student_commune_name <- school_yes %>% group_by(student_commune_name.school) %>%
  summarise(count = n()) %>% mutate(freq = count/sum(count)) %>%
  # Would need to merge to a list of commune names and numbers if want to display all communes for all matched statuses
  #merge(commune_, by = "commune_num", all = TRUE) %>% 
  mutate(matched = 1) 
school_match_no.student_commune_name <- school_no %>% group_by(student_commune_name.school) %>%
  summarise(count = n()) %>% mutate(freq = count/sum(count)) %>%
  #merge(commune_nums, by = "commune_num", all = TRUE) %>% 
  mutate(matched = 0)

school_match.student_commune_name <- rbind(school_match_yes.student_commune_name, school_match_no.student_commune_name) %>%
  arrange(student_commune_name.school, matched)

ggplot(school_match.student_commune_name) +
  geom_col(aes(x = as.factor(matched), y = freq, fill = as.factor(matched))) +
  facet_wrap(~student_commune_name.school, scales = "fixed") +
  #facet_wrap(~student_commune_name.school, scales = "free") +
  labs(title = "Matching of school record to clinical record by commune",
       x = "Matched status",
       y = "Feature frequency",
       fill = "Matched status")
# most of the difference in matched commune frequency is for Temuco which is the biggest commune.


ggplot(ks_perm.school.pvals, aes(x = commune_code, y = after_stat(density))) +
  geom_density() +
  geom_vline(xintercept = ks.school.commune_code$p.value, color = "red")

# Results for ses status
school_match_yes.ses_status <- school_yes %>% group_by(ses_status.school) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 1)
school_match_no.ses_status <- school_no %>% group_by(ses_status.school) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 0)
school_match.ses_status <- rbind(school_match_yes.ses_status, school_match_no.ses_status) %>%
  arrange(ses_status.school, matched)

ggplot(school_match.ses_status) +
  geom_col(aes(x = as.factor(matched), y = freq, fill = as.factor(matched))) +
  facet_wrap(~ses_status.school) +
  labs(title = "Matching of school record to clinical record by SES status",
       x = "Matched status",
       y = "Feature frequency",
       fill = "Matched status")

ggplot(ks_perm.school.pvals, aes(x = ses_status, y = after_stat(density))) +
  geom_density() +
  geom_vline(xintercept = ks.school.ses_status$p.value, color = "red")


```

Bit easier to match SES status of 1 (probably more common)

Our matched/non-matched are not different by sex (p-value in Kolmog is same as most of distribution of permuted pvals) but are different by commune and ses status. Cohen's D test isn't suitable to compare the matched and un-matched because the data don't have standard deviations.

??Add commune maps here with size of sample for school and clinical?? Also size of other features.



```{r kolmogorov tests patient, warning = FALSE}

patients_yes <- patients_matched_small %>% filter(matched == 1) #%>% select(sex.school)
patients_no <- patients_matched_small %>% filter(matched == 0)

# Kolmogorov tests for our matched results
ks.patients.sex <- ks.test(na.omit(patients_yes$sex.patient),
                         na.omit(patients_no$sex.patient),
                         alternative = "two.sided", simulate.p.value = TRUE)
ks.patients.sex

ks.patients.ses_status <- ks.test(as.numeric(na.omit(patients_yes$ses_status.patient)),
                                as.numeric(na.omit(patients_no$ses_status.patient)),
                                alternative = "two.sided", simulate.p.value = TRUE)
ks.patients.ses_status

ks.patients.commune_code<- ks.test(as.numeric(na.omit(patients_yes$commune_code)),
                                 as.numeric(na.omit(patients_no$commune_code)),
                                 alternative = "two.sided", simulate.p.value = TRUE)
ks.patients.commune_code


# Kolmogorov tests with permutation distributions
set.seed(123)
nPerm <- 200 # change to 2000
ks_perm.patients.pvals <- data.frame(sex = numeric(nPerm),
                                   commune_code = numeric(nPerm),
                                   ses_status = numeric(nPerm))

patients_matched_small_perm <- patients_matched_small

for (i in 1:nPerm) {
  #print(i)
  patients_matched_small_perm$matched <- patients_matched_small$matched[sample(nrow(patients_matched_small))] # permute matched status
  patients_perm_yes <- patients_matched_small_perm %>% filter(matched == 1)
  patients_perm_no <- patients_matched_small_perm %>% filter(matched == 0)
  
  ks_perm.patients.sex <- ks.test(na.omit(patients_perm_yes$sex.patient),
                                na.omit(patients_perm_no$sex.patient), 
                                alternative = "two.sided")
  ks_perm.patients.commune_code <- ks.test(as.numeric(na.omit(patients_perm_yes$commune_code)),
                                        as.numeric(na.omit(patients_perm_no$commune_code)),
                                        alternative = "two.sided")
  ks_perm.patients.ses_status <- ks.test(as.numeric(na.omit(patients_perm_yes$ses_status.patient)),
                                       as.numeric(na.omit(patients_perm_no$ses_status.patient)),
                                       alternative = "two.sided")
  
  ks_perm.patients.pvals$sex[i] <- ks_perm.patients.sex$p.value
  ks_perm.patients.pvals$commune_code[i] <- ks_perm.patients.commune_code$p.value
  ks_perm.patients.pvals$ses_status[i] <- ks_perm.patients.ses_status$p.value
}

# Results for sex
patients_match_yes.sex <- patients_yes %>% group_by(sex.patient) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 1)
patients_match_no.sex <- patients_no %>% group_by(sex.patient) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 0)
patients_match.sex <- rbind(patients_match_yes.sex, patients_match_no.sex) %>%
  mutate(sex_desc = ifelse(sex.patient == 1, "Male", ifelse(sex.patient == 2, "Female", NA))) %>% 
  arrange(sex_desc, matched)

ggplot(patients_match.sex) +
  geom_col(aes(x = as.factor(matched), y = freq, fill = as.factor(matched))) +
  facet_wrap(~sex_desc) +
  labs(title = "Matching of clinical record to school record by sex",
       x = "Matched status",
       y = "Feature frequency",
       fill = "Matched status")

ggplot(ks_perm.patients.pvals, aes(x = sex, y = after_stat(density))) +
  geom_density() +
  geom_vline(xintercept = ks.patients.sex$p.value, color = "red")

# Results for commune
patients_match_yes.student_commune_name <- patients_yes %>% group_by(student_commune_name.patient) %>%
  summarise(count = n()) %>% mutate(freq = count/sum(count)) %>%
  # Would need to merge to a list of commune names and numbers if want to display all communes for all matched statuses
  #merge(commune_, by = "commune_num", all = TRUE) %>% 
  mutate(matched = 1) 
patients_match_no.student_commune_name <- patients_no %>% group_by(student_commune_name.patient) %>%
  summarise(count = n()) %>% mutate(freq = count/sum(count)) %>%
  #merge(commune_nums, by = "commune_num", all = TRUE) %>% 
  mutate(matched = 0)

patients_match.student_commune_name <- rbind(patients_match_yes.student_commune_name, patients_match_no.student_commune_name) %>%
  arrange(student_commune_name.patient, matched)

ggplot(patients_match.student_commune_name) +
  geom_col(aes(x = as.factor(matched), y = freq, fill = as.factor(matched))) +
  facet_wrap(~student_commune_name.patient, scales = "fixed") +
  #facet_wrap(~student_commune_name.school, scales = "free") +
  labs(title = "Matching of clinical record to school record by commune",
       x = "Matched status",
       y = "Feature frequency",
       fill = "Matched status")
# most of the difference in matched commune frequency is for Temuco which is the biggest commune.


ggplot(ks_perm.patients.pvals, aes(x = commune_code, y = after_stat(density))) +
  geom_density() +
  geom_vline(xintercept = ks.patients.commune_code$p.value, color = "red")

# Results for ses status
patients_match_yes.ses_status <- patients_yes %>% group_by(ses_status.patient) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 1)
patients_match_no.ses_status <- patients_no %>% group_by(ses_status.patient) %>% summarise(count = n()) %>% mutate(freq = count/sum(count), matched = 0)
patients_match.ses_status <- rbind(patients_match_yes.ses_status, patients_match_no.ses_status) %>%
  arrange(ses_status.patient, matched)

ggplot(patients_match.ses_status) +
  geom_col(aes(x = as.factor(matched), y = freq, fill = as.factor(matched))) +
  facet_wrap(~ses_status.patient) +
  labs(title = "Matching of clinical record to school record by SES status",
       x = "Matched status",
       y = "Feature frequency",
       fill = "Matched status")

ggplot(ks_perm.patients.pvals, aes(x = ses_status, y = after_stat(density))) +
  geom_density() +
  geom_vline(xintercept = ks.patients.ses_status$p.value, color = "red")


```

TODO - comment on whether any of the matched patients had only intellectual disability and not autism.

### Prev delta

```{r new prev}
n_aut_araucS <- nrow(school_matched) + length(unique(patients_matched$patient_id)) - nrow(matches) # Use this version because accounts for non-unique patients with both match and non-match
#n_aut_araucS <- school_matched_small %>% filter(matched == 0) %>% nrow() +
#  dim(patients_matched_small %>% filter(matched == 0) %>% select(patient_id) %>% unique())[1] + nrow(matches)
```

## Frequentist prevalence estimation

### Autism and ADHD prevalence by sex

```{r adj prev}
# Autism
aut_prev <- get_grouped_prev(x = chile_bayes_aut, stdpop = chile_stdpop, 
                             grouping_vars = c("age_june30", "age_cat_name", "sex", "sex_desc", "autism"),
                             disease = "autism")

aut_prev_adj <- aut_prev %>% # Don't use get_adjusted_prev here because we have no variables to group on
  summarise(sum_sample_pop_size = sum(sample_pop_size),
            crude_rate = sum(n_disease) / sum(sample_pop_size),
            crude_count = sum(n_disease),
            adjusted_rate = sum(n_disease / sample_pop_size * pop_prop),
            adjusted_count = round(adjusted_rate * sum_sample_pop_size, 0), # had to fudge this to get MCMC to run bc it needs integers
            #adjusted_count = adjusted_rate * sum_sample_pop_size,
            var = sum(pop_prop^2 * n_disease / sample_pop_size^2),
            #se2 = sqrt(sum((std_pop/sum(std_pop))^2 * n_autism/sample_pop_size^2)),
            w_M = max(w),
            crude_ci_lower = crude_rate - (1.96 * sqrt(crude_rate * (1 - crude_rate) / sum_sample_pop_size)),
            crude_ci_upper = crude_rate + (1.96 * sqrt(crude_rate * (1 - crude_rate) / sum_sample_pop_size)),
            adjusted_ci_lower = ifelse(var == 0, 0, var / (2*adjusted_rate) * qchisq(p = 0.05/2, df = 2*adjusted_rate^2 / var)),
            adjusted_ci_upper = (var + w_M^2) / (2*(adjusted_rate + w_M)) * qchisq(p = 1-0.05/2, df = 2*(adjusted_rate+w_M)^2 / (var+w_M^2))) %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

aut_prev_adj %>% 
  select(crude_ci_lower, crude_rate, crude_ci_upper,
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
  mutate(across(is.numeric, round, digits = 5))

# ADHD
adhd_prev <- get_grouped_prev(x = chile_bayes_adhd, stdpop = chile_stdpop, 
                             grouping_vars = c("age_june30", "age_cat_name", "sex", "sex_desc", "adhd"),
                             disease = "adhd")

adhd_prev_adj <- adhd_prev %>% # Don't use get_adjusted_prev here because we have no variables to group on
  summarise(sum_sample_pop_size = sum(sample_pop_size),
            crude_rate = sum(n_disease) / sum(sample_pop_size),
            crude_count = sum(n_disease),
            adjusted_rate = sum(n_disease / sample_pop_size * pop_prop),
            adjusted_count = round(adjusted_rate * sum_sample_pop_size, 0), # had to fudge this to get MCMC to run bc it needs integers
            #adjusted_count = adjusted_rate * sum_sample_pop_size,
            var = sum(pop_prop^2 * n_disease / sample_pop_size^2),
            #se2 = sqrt(sum((std_pop/sum(std_pop))^2 * n_autism/sample_pop_size^2)),
            w_M = max(w),
            crude_ci_lower = crude_rate - (1.96 * sqrt(crude_rate * (1 - crude_rate) / sum_sample_pop_size)),
            crude_ci_upper = crude_rate + (1.96 * sqrt(crude_rate * (1 - crude_rate) / sum_sample_pop_size)),
            adjusted_ci_lower = ifelse(var == 0, 0, var / (2*adjusted_rate) * qchisq(p = 0.05/2, df = 2*adjusted_rate^2 / var)),
            adjusted_ci_upper = (var + w_M^2) / (2*(adjusted_rate + w_M)) * qchisq(p = 1-0.05/2, df = 2*(adjusted_rate+w_M)^2 / (var+w_M^2))) %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

adhd_prev_adj %>% 
  select(crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
  mutate(across(is.numeric, round, digits = 5))

```


```{r adj prev sex}
chile_stdpop_f <- chile_stdpop %>%
  filter(sex == 2) %>%
  mutate(pop_prop = std_pop / sum(std_pop))
chile_stdpop_m <- chile_stdpop %>%
  filter(sex == 1) %>%
  mutate(pop_prop = std_pop / sum(std_pop))

# Autism
aut_prev_f <- chile_bayes_aut %>%
  filter(sex == 2) %>%
  get_grouped_prev(stdpop = chile_stdpop_f, grouping_vars = c("age_june30", "sex", "autism"), disease = "autism")
aut_prev_adj_f <- get_adjusted_prev(aut_prev_f, grouping_vars = c()) %>% mutate(sex_desc = "Female") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

aut_prev_m <- chile_bayes_aut %>%
  filter(sex == 1) %>%
  get_grouped_prev(stdpop = chile_stdpop_m, grouping_vars = c("age_june30", "sex", "autism"), disease = "autism")
aut_prev_adj_m <- get_adjusted_prev(aut_prev_m, grouping_vars = c()) %>% mutate(sex_desc = "Male") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

rbind(aut_prev_adj_m, aut_prev_adj_f) %>% 
  select(sex_desc, 
         crude_ci_lower, crude_rate, crude_ci_upper,
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
  mutate(across(is.numeric, round, digits = 5)) 

# ADHD
adhd_prev_f <- chile_bayes_adhd %>%
  filter(sex == 2) %>%
  get_grouped_prev(stdpop = chile_stdpop_f, grouping_vars = c("age_june30", "sex", "adhd"), disease = "adhd")
adhd_prev_adj_f <- get_adjusted_prev(adhd_prev_f, grouping_vars = c()) %>% mutate(sex_desc = "Female") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

adhd_prev_m <- chile_bayes_adhd %>%
  filter(sex == 1) %>%
  get_grouped_prev(stdpop = chile_stdpop_m, grouping_vars = c("age_june30", "sex", "adhd"), disease = "adhd")
adhd_prev_adj_m <- get_adjusted_prev(adhd_prev_m, grouping_vars = c()) %>% mutate(sex_desc = "Male") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

rbind(adhd_prev_adj_m, adhd_prev_adj_f) %>%
  select(sex_desc,
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
  mutate(across(is.numeric, round, digits = 5)) 
  #mutate(across(is.numeric, signif, digits = 3))

```

```{r adj prev plot aut agecat, fig.cap = "Sample prevalence of autism by age band and sex. Bars show 95% normal confidence intervals."}
# Autism
aut_prev.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_aut, 
                                          grouping_vars = c("age_cat_name", "sex_desc", "autism"),
                                          disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

# By age category and sex
ggplot(data = aut_prev.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  labs(title = "Autism prevalence",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age band")
```


```{r adj prev plot aut rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of autism, by sex and in aggregate. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All 
aut_prev_adj.long <- aut_prev_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

aut_prev_adj.long_plot <- ggplot(data = aut_prev_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  labs(title = "",
       #y = "Aggregate prevalence",
       fill = "Prevalence")

# Females
aut_prev_adj_f.long <- aut_prev_adj_f %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

# Males
aut_prev_adj_m.long <- aut_prev_adj_m %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

# Both
aut_prev_adj_b.long <- rbind(aut_prev_adj_m.long, aut_prev_adj_f.long)

aut_prev_adj_b.long_plot <- ggplot(data = aut_prev_adj_b.long) +
  geom_col(aes(x = sex_desc, y = rate, fill = type), position = position_dodge(), show.legend = FALSE) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Autism prevalence",
       y = "Aggregate prevalence")

grid.arrange(aut_prev_adj_b.long_plot, aut_prev_adj.long_plot, ncol = 2)
```



```{r adj prev plot adhd agecat, fig.cap = "Sample prevalence of ADHD by age band and sex. Bars show 95% normal confidence intervals."}
# ADHD
adhd_prev.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_adhd, 
                                          grouping_vars = c("age_cat_name", "sex_desc", "adhd"),
                                          disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

# By age category and sex
ggplot(data = adhd_prev.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  labs(title = "ADHD prevalence",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age band")
```


```{r adj prev plot adhd rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of ADHD, by sex and in aggregate. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}
# All
adhd_prev_adj.long <- adhd_prev_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

adhd_prev_adj.long_plot <- ggplot(data = adhd_prev_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  labs(title = "",
       #y = "Aggregate prevalence",
       fill = "Prevalence")

# Females
adhd_prev_adj_f.long <- adhd_prev_adj_f %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

# Males
adhd_prev_adj_m.long <- adhd_prev_adj_m %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

# Both
adhd_prev_adj_b.long <- rbind(adhd_prev_adj_m.long, adhd_prev_adj_f.long)

adhd_prev_adj_b.long_plot <- ggplot(data = adhd_prev_adj_b.long) +
  geom_col(aes(x = sex_desc, y = rate, fill = type), position = position_dodge(), show.legend = FALSE) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank()) +
  labs(title = "ADHD prevalence",
       y = "Aggregate prevalence")

grid.arrange(adhd_prev_adj_b.long_plot, adhd_prev_adj.long_plot, ncol = 2)

```

### Autism and ADHD prevalence by health service

```{r adj prev health aut}
aut_prev_health <- get_grouped_prev(x = chile_bayes_aut, stdpop = chile_stdpop, 
                                    grouping_vars = c("health_service_code", "age_june30", "age_cat_name", "sex", "sex_desc", "autism"),
                                    disease = "autism")

aut_prev_health_adj <- get_adjusted_prev(aut_prev_health, grouping_vars = "health_service_code") %>%
  merge(health_service_lookup, by = "health_service_code") %>%
  rename(health_service_name_long = health_service_name,
         health_service_name = health_service_name_short) %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

aut_prev_health_adj %>% 
  select(health_service_name, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))

```


```{r adj prev health plot aut agecat, fig.cap = "Sample prevalence of autism by health service, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
aut_prev_health.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_aut,
                                                    grouping_vars = c("health_service_name", "age_cat_name", "sex_desc", "autism"),
                                                    disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_health.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~health_service_name) +
  labs(title = "Autism prevalence by health service",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev health plot aut rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of autism by health service. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
aut_prev_health_adj.long <- aut_prev_health_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = aut_prev_health_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~health_service_name) +
  labs(title = "Autism prevalence by health service",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```

```{r adj prev health adhd}
adhd_prev_health <- get_grouped_prev(x = chile_bayes_adhd, stdpop = chile_stdpop, 
                                    grouping_vars = c("health_service_code", "age_june30", "age_cat_name", "sex", "sex_desc", "adhd"),
                                    disease = "adhd")

adhd_prev_health_adj <- get_adjusted_prev(adhd_prev_health, grouping_vars = "health_service_code") %>%
  merge(health_service_lookup, by = "health_service_code") %>%
  rename(health_service_name_long = health_service_name,
         health_service_name = health_service_name_short) %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

adhd_prev_health_adj %>% 
  select(health_service_name, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))  

```


```{r adj prev health plot adhd agecat, fig.cap = "Sample prevalence of ADHD by health service, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
adhd_prev_health.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_adhd,
                                                    grouping_vars = c("health_service_name", "age_cat_name", "sex_desc", "adhd"),
                                                    disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_health.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~health_service_name) +
  labs(title = "ADHD prevalence by health service",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev health plot adhd rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of ADHD by health service. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
adhd_prev_health_adj.long <- adhd_prev_health_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = adhd_prev_health_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~health_service_name) +
  labs(title = "ADHD prevalence by health service",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```

```{r adj prev araucS}
# Only do autism here because we only have clinical data for autism
chile_bayes_aut_araucS <- chile_bayes_aut %>%
  filter(health_service_code == 5)

aut_prev_araucS <- get_grouped_prev(x = chile_bayes_aut_araucS, stdpop = chile_stdpop, 
                                    grouping_vars = c("commune_name", "age_june30", "age_cat_name", "sex", "sex_desc", "autism"),
                                    disease = "autism")

aut_prev_araucS_adj <- get_adjusted_prev(aut_prev_araucS, grouping_vars = "commune_name") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

aut_prev_araucS_adj %>% 
  select(commune_name, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
  mutate(across(is.numeric, round, digits = 5)) 
```

```{r adj prev araucS plot aut agecat, fig.cap = "Sample prevalence of autism by commune in Araucanía Sur health service, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
aut_prev_araucS.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_aut_araucS,
                                                    grouping_vars = c("commune_name", "age_cat_name", "sex_desc", "autism"),
                                                    disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_araucS.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  facet_wrap(~commune_name) +
  labs(title = "Autism prevalence by commune in Araucanía Sur",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev araucS plot aut rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of autism by commune in Araucanía Sur health service. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}
# All
aut_prev_araucS_adj.long <- aut_prev_araucS_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = aut_prev_araucS_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~commune_name) +
  labs(title = "Autism prevalence by commune in Araucanía Sur",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```

### Autism and ADHD prevalence by socio-economic status

```{r adj prev economicAll aut}
aut_prev_econA <- get_grouped_prev(x = chile_bayes_aut, stdpop = chile_stdpop, 
                                    grouping_vars = c("school_fee", "age_june30", "age_cat_name", "sex", "sex_desc", "autism"),
                                    disease = "autism")

aut_prev_econA_adj <- get_adjusted_prev(aut_prev_econA, grouping_vars = "school_fee") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

aut_prev_econA_adj %>% 
  select(school_fee, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))  

```


```{r adj prev economicAll plot aut agecat, fig.cap = "Sample prevalence of autism by socio-economic (SES) status of student's family, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
aut_prev_econA.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_aut,
                                                    grouping_vars = c("school_fee", "age_cat_name", "sex_desc", "autism"),
                                                    disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_econA.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_fee) +
  labs(title = "Autism prevalence by SES status",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev economicAll plot aut rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of autism by socio-economic (SES) status of student's family. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
aut_prev_econA_adj.long <- aut_prev_econA_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = aut_prev_econA_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~school_fee) +
  labs(title = "Autism prevalence by SES status",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```

```{r adj prev economicAll adhd}
adhd_prev_econA <- get_grouped_prev(x = chile_bayes_adhd, stdpop = chile_stdpop, 
                                    grouping_vars = c("school_fee", "age_june30", "age_cat_name", "sex", "sex_desc", "adhd"),
                                    disease = "adhd")

adhd_prev_econA_adj <- get_adjusted_prev(adhd_prev_econA, grouping_vars = "school_fee")  %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

adhd_prev_econA_adj %>% 
  select(school_fee, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))  

```


```{r adj prev economicAll plot adhd agecat, fig.cap = "Sample prevalence of ADHD by socio-economic (SES) status of student's family, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
adhd_prev_econA.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_adhd,
                                                    grouping_vars = c("school_fee", "age_cat_name", "sex_desc", "adhd"),
                                                    disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_econA.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_fee) +
  labs(title = "ADHD prevalence by SES status",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev economicAll plot adhd rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of ADHD by socio-economic (SES) status of student's family. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
adhd_prev_econA_adj.long <- adhd_prev_econA_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = adhd_prev_econA_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~school_fee) +
  labs(title = "ADHD prevalence by SES status",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```

### Autism and ADHD prevalence by ethnicity

```{r adj prev ethnicity aut}
aut_prev_ethnic <- get_grouped_prev(x = chile_bayes_aut, stdpop = chile_stdpop, 
                                    grouping_vars = c("ethnic_2_group", "age_june30", "age_cat_name", "sex", "sex_desc", "autism"),
                                    disease = "autism")

aut_prev_ethnic_adj <- get_adjusted_prev(aut_prev_ethnic, grouping_vars = "ethnic_2_group") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

aut_prev_ethnic_adj %>% 
  select(ethnic_2_group, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))  

```


```{r adj prev ethnicity plot aut agecat, fig.cap = "Sample prevalence of autism by ethnicity, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
aut_prev_ethnic.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_aut,
                                                    grouping_vars = c("ethnic_2_group", "age_cat_name", "sex_desc", "autism"),
                                                    disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_ethnic.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~ethnic_2_group) +
  labs(title = "Autism prevalence by ethnicity",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev ethnicity plot aut rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of autism by ethnicity. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
aut_prev_ethnic_adj.long <- aut_prev_ethnic_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = aut_prev_ethnic_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~ethnic_2_group) +
  labs(title = "Autism prevalence by ethnicity",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```

```{r adj prev ethnicity adhd}
adhd_prev_ethnic <- get_grouped_prev(x = chile_bayes_adhd, stdpop = chile_stdpop, 
                                    grouping_vars = c("ethnic_2_group", "age_june30", "age_cat_name", "sex", "sex_desc", "adhd"),
                                    disease = "adhd")

adhd_prev_ethnic_adj <- get_adjusted_prev(adhd_prev_ethnic, grouping_vars = "ethnic_2_group")  %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

adhd_prev_ethnic_adj %>% 
  select(ethnic_2_group, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))  

```


```{r adj prev ethnicity plot adhd agecat, fig.cap = "Sample prevalence of ADHD by ethnicity, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
adhd_prev_ethnic.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_adhd,
                                                    grouping_vars = c("ethnic_2_group", "age_cat_name", "sex_desc", "adhd"),
                                                    disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_ethnic.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~ethnic_2_group) +
  labs(title = "ADHD prevalence by ethnicity",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev ethnicity plot adhd rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of ADHD by ethnicity. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
adhd_prev_ethnic_adj.long <- adhd_prev_ethnic_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = adhd_prev_ethnic_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~ethnic_2_group) +
  labs(title = "ADHD prevalence by ethnicity",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```


### Autism and ADHD prevalence by rurality

```{r adj prev rurality aut}
aut_prev_rural <- get_grouped_prev(x = chile_bayes_aut, stdpop = chile_stdpop, 
                                    grouping_vars = c("school_rurality", "age_june30", "age_cat_name", "sex", "sex_desc", "autism"),
                                    disease = "autism")

aut_prev_rural_adj <- get_adjusted_prev(aut_prev_rural, grouping_vars = "school_rurality") %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

aut_prev_rural_adj %>% 
  select(school_rurality, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))  

```


```{r adj prev rurality plot aut agecat, fig.cap = "Sample prevalence of autism by school's rurality, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
aut_prev_rural.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_aut,
                                                    grouping_vars = c("school_rurality", "age_cat_name", "sex_desc", "autism"),
                                                    disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_rural.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_rurality) +
  labs(title = "Autism prevalence by school's rurality",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev rurality plot aut rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of autism by school's rurality. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
aut_prev_rural_adj.long <- aut_prev_rural_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = aut_prev_rural_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~school_rurality) +
  labs(title = "Autism prevalence by school's rurality",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```

```{r adj prev rurality adhd}
adhd_prev_rural <- get_grouped_prev(x = chile_bayes_adhd, stdpop = chile_stdpop, 
                                    grouping_vars = c("school_rurality", "age_june30", "age_cat_name", "sex", "sex_desc", "adhd"),
                                    disease = "adhd")

adhd_prev_rural_adj <- get_adjusted_prev(adhd_prev_rural, grouping_vars = "school_rurality")  %>%
  mutate(crude_ci_lower = ifelse(crude_ci_lower < 0, 0, crude_ci_lower),
         adjusted_ci_lower = ifelse(adjusted_ci_lower < 0, 0, adjusted_ci_lower))

adhd_prev_rural_adj %>% 
  select(school_rurality, 
         crude_ci_lower, crude_rate, crude_ci_upper, 
         adjusted_ci_lower, adjusted_rate, adjusted_ci_upper) %>%
 mutate(across(is.numeric, round, digits = 5))  

```


```{r adj prev rurality plot adhd agecat, fig.cap = "Sample prevalence of ADHD by school's rurality, age band and sex. Bars show 95% normal confidence intervals."}
# By age and sex
# Age categories
adhd_prev_rural.agecat.sex <- get_grouped_prev_plot(x = chile_bayes_adhd,
                                                    grouping_vars = c("school_rurality", "age_cat_name", "sex_desc", "adhd"),
                                                    disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_rural.agecat.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_cat_name, fill = age_cat_name), position = "dodge") +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_cat_name), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_d(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_rurality) +
  labs(title = "ADHD prevalence by school's rurality",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age category")
```


```{r adj prev rurality plot adhd rate, fig.cap = "Crude and age- and sex-adjusted sample prevalences of ADHD by school's rurality. Bars for crude prevalence show 95% normal confidence intervals and bars for adjusted prevalence show 95% gamma confidence intervals."}

# All
adhd_prev_rural_adj.long <- adhd_prev_rural_adj %>%
  select(-sum_sample_pop_size, -crude_count, -adjusted_count, -var, -w_M) %>%
  pivot_longer(cols = c(crude_rate, adjusted_rate, crude_ci_lower, crude_ci_upper, adjusted_ci_lower, adjusted_ci_upper),
               names_to = c("type", ".value"),
               names_pattern = "(crude|adjusted)_(.*)") %>%
  mutate(type = factor(type, levels = c("crude", "adjusted"), labels = c("Crude", "Adjusted")))

ggplot(data = adhd_prev_rural_adj.long) +
  geom_col(aes(x = type, y = rate, fill = type), position = position_dodge(), show.legend = TRUE) +
  geom_errorbar(aes(x = type, ymin = ci_lower, ymax = ci_upper, group = type), width = 0.2, position = position_dodge(width = 0.9)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  facet_wrap(~school_rurality) +
  labs(title = "ADHD prevalence by rurality",
       #y = "Aggregate prevalence",
       fill = "Prevalence")
```


## Bayesian prevalence estimation

```{r bayes global params}
nObs <- nrow(chile_bayes)
nIter <- 1000
nBurn <- 1000
pars <- c("theta_a", "theta_b", "theta", "disease_sample", "disease_pred")

# Autism priors
# All
aut_theta_mu_prior <- aut_prev_adj$adjusted_rate
aut_theta_sigma_prior <- (aut_prev_adj$adjusted_ci_upper - aut_prev_adj$adjusted_ci_lower) / (2*1.96)
# Females
aut_theta_mu_prior_f <- aut_prev_adj_f$adjusted_rate
aut_theta_sigma_prior_f <- sqrt(aut_prev_adj_f$var)
# Males
theta_mu_prior_m <- aut_prev_adj_m$adjusted_rate
theta_sigma_prior_m <- sqrt(aut_prev_adj_m$var)
# Projections, use same sigma as before
aut_theta_mu_proj <- c(0.005, 0.01, 0.02, 0.03) # 0.5%, 1%, 2%, 3% prevalence
aut_theta_mu_proj_f <- c(0.0025, 0.005, 0.01, 0.02)
aut_theta_mu_proj_m <- c(0.01, 0.02, 0.03, 0.05)
aut_theta_sigma_proj <- c(rep((aut_prev_adj$adjusted_ci_upper - aut_prev_adj$adjusted_ci_lower) / (2*1.96), 4))

# ADHD priors
# All
adhd_theta_mu_prior <- adhd_prev_adj$adjusted_rate
adhd_theta_sigma_prior <- (adhd_prev_adj$adjusted_ci_upper - adhd_prev_adj$adjusted_ci_lower) / (2*1.96)
# Females
adhd_theta_mu_prior_f <- adhd_prev_adj_f$adjusted_rate
adhd_theta_sigma_prior_f <- sqrt(adhd_prev_adj_f$var)
# Males
adhd_theta_mu_prior_m <- adhd_prev_adj_m$adjusted_rate
adhd_theta_sigma_prior_m <- sqrt(adhd_prev_adj_m$var)
# Projections, use same sigma as before
adhd_theta_mu_proj <- c(0.02, 0.03, 0.05, 0.07) # 2%, 3%, 5%, 7% prevalence
adhd_theta_mu_proj_f <- c(0.015, 0.02, 0.03, 0.05)
adhd_theta_mu_proj_m <- c(0.02, 0.03, 0.05, 0.07)
adhd_theta_sigma_proj <- c(rep((adhd_prev_adj$adjusted_ci_upper - adhd_prev_adj$adjusted_ci_lower) / (2*1.96), 4))

rand_model <- "model {
  for(i in 1:nFeat) { # For each category in the feature grouping
    theta[i] ~ dbeta(theta_a, theta_b)
    disease_sample[i] ~ dbin(theta[i], nObs[i])
    disease_pred[i] ~ dbin(theta[i], nObs[i])
  }
}"
```

### Random effect on sex

```{r bayes sex aut, fig.cap = "Posterior predictive distribution for autism with a random effect on sex, and with age- and sex-adjusted global prevalence prior."}
aut_prev_sex_adj <- rbind(aut_prev_adj_m, aut_prev_adj_f) 
# have to put m first because 1 comes before 2 and otherwise will mess up naming in do_jags_rand_model

aut_prev_sex_post <- do_jags_rand_model(x = aut_prev_sex_adj,
                              feat = "sex_desc",
                              model = rand_model,
                              theta_mu = aut_theta_mu_prior,
                              theta_sigma = aut_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("sex_desc" = "Feat_names")

plot_post_density(aut_prev_sex_post, aut_prev_sex_adj, 
                  feat = "sex_desc", 
                  theta_mu = aut_theta_mu_prior, theta_sigma = aut_theta_sigma_prior,
                  disease = "Autism")
```


```{r bayes sex adhd, fig.cap = "Posterior predictive distribution for ADHD with a random effect on sex, and with age- and sex-adjusted global prevalence prior."}
adhd_prev_sex_adj <- rbind(adhd_prev_adj_m, adhd_prev_adj_f) 
# have to put m first because 1 comes before 2 and otherwise will mess up naming in do_jags_rand_model

adhd_prev_sex_post <- do_jags_rand_model(x = adhd_prev_sex_adj,
                              feat = "sex_desc",
                              model = rand_model,
                              theta_mu = adhd_theta_mu_prior,
                              theta_sigma = adhd_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("sex_desc" = "Feat_names")

plot_post_density(adhd_prev_sex_post, adhd_prev_sex_adj, 
                  feat = "sex_desc", 
                  theta_mu = adhd_theta_mu_prior, theta_sigma = adhd_theta_sigma_prior,
                  disease = "ADHD")
```

### Random effect on health service

```{r bayes health aut, fig.cap = "Posterior predictive distribution for autism with a random effect on student's health service, and with age- and sex-adjusted global prevalence prior."}
aut_prev_health_post <- do_jags_rand_model(x = aut_prev_health_adj,
                              feat = "health_service_name",
                              model = rand_model,
                              theta_mu = aut_theta_mu_prior,
                              theta_sigma = aut_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("health_service_name" = "Feat_names")

plot_post_density(aut_prev_health_post, aut_prev_health_adj, 
                  feat = "health_service_name", 
                  theta_mu = aut_theta_mu_prior, theta_sigma = aut_theta_sigma_prior,
                  disease = "Autism")
```

```{r bayes health adhd, fig.cap = "Posterior predictive distribution for ADHD with a random effect on health service, and with age- and sex-adjusted global prevalence prior."}
adhd_prev_health_post <- do_jags_rand_model(x = adhd_prev_health_adj,
                              feat = "health_service_name",
                              model = rand_model,
                              theta_mu = adhd_theta_mu_prior,
                              theta_sigma = adhd_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("health_service_name" = "Feat_names")

plot_post_density(adhd_prev_health_post, adhd_prev_health_adj, 
                  feat = "health_service_name", 
                  theta_mu = adhd_theta_mu_prior, theta_sigma = adhd_theta_sigma_prior,
                  disease = "ADHD")
```

### Random effect on commune in Araucanía Sur health service

```{r bayes araucS aut, fig.cap = "Posterior predictive distribution for autism with a random effect on commune within Araucanía Sur health service, and with age- and sex-adjusted global prevalence prior."}
aut_prev_araucS_post <- do_jags_rand_model(x = aut_prev_araucS_adj,
                              feat = "commune_name",
                              model = rand_model,
                              theta_mu = aut_theta_mu_prior,
                              theta_sigma = aut_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("commune_name" = "Feat_names")

plot_post_density(aut_prev_araucS_post, aut_prev_araucS_adj, 
                  feat = "commune_name", 
                  theta_mu = aut_theta_mu_prior, theta_sigma = aut_theta_sigma_prior,
                  disease = "Autism")
```

### Random effect on socio-economic status

```{r bayes economicAll aut, fig.cap = "Posterior predictive distribution for autism with a random effect on socio-economic status of student's family, and with age- and sex-adjusted global prevalence prior."}
aut_prev_econA_post <- do_jags_rand_model(x = aut_prev_econA_adj,
                              feat = "school_fee",
                              model = rand_model,
                              theta_mu = aut_theta_mu_prior,
                              theta_sigma = aut_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("school_fee" = "Feat_names")

plot_post_density(aut_prev_econA_post, aut_prev_econA_adj, 
                  feat = "school_fee", 
                  theta_mu = aut_theta_mu_prior, theta_sigma = aut_theta_sigma_prior,
                  disease = "Autism")
```

```{r bayes economicAll adhd, fig.cap = "Posterior predictive distribution for ADHD with a random effect on socio-economic status of student's family, and with age- and sex-adjusted global prevalence prior."}
adhd_prev_econA_post <- do_jags_rand_model(x = adhd_prev_econA_adj,
                              feat = "school_fee",
                              model = rand_model,
                              theta_mu = adhd_theta_mu_prior,
                              theta_sigma = adhd_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("school_fee" = "Feat_names")

plot_post_density(adhd_prev_econA_post, adhd_prev_econA_adj, 
                  feat = "school_fee", 
                  theta_mu = adhd_theta_mu_prior, theta_sigma = adhd_theta_sigma_prior,
                  disease = "ADHD")
```

### Random effect on ethnicity

```{r bayes ethnicity aut, fig.cap = "Posterior predictive distribution for autism with a random effect on ethnicity, and with age- and sex-adjusted global prevalence prior."}
aut_prev_ethnic_post <- do_jags_rand_model(x = aut_prev_ethnic_adj,
                              feat = "ethnic_2_group",
                              model = rand_model,
                              theta_mu = aut_theta_mu_prior,
                              theta_sigma = aut_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("ethnic_2_group" = "Feat_names")

plot_post_density(aut_prev_ethnic_post, aut_prev_ethnic_adj, 
                  feat = "ethnic_2_group", 
                  theta_mu = aut_theta_mu_prior, theta_sigma = aut_theta_sigma_prior,
                  disease = "Autism")
```

```{r bayes ethnic adhd, fig.cap = "Posterior predictive distribution for ADHD with a random effect on ethnicity, and with age- and sex-adjusted global prevalence prior."}
adhd_prev_ethnic_post <- do_jags_rand_model(x = adhd_prev_ethnic_adj,
                              feat = "ethnic_2_group",
                              model = rand_model,
                              theta_mu = adhd_theta_mu_prior,
                              theta_sigma = adhd_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("ethnic_2_group" = "Feat_names")

plot_post_density(adhd_prev_ethnic_post, adhd_prev_ethnic_adj, 
                  feat = "ethnic_2_group", 
                  theta_mu = adhd_theta_mu_prior, theta_sigma = adhd_theta_sigma_prior,
                  disease = "ADHD")
```

### Random effect on school's rurality

```{r bayes rurality aut, fig.cap = "Posterior predictive distribution for autism with a random effect on school's rurality, and with age- and sex-adjusted global prevalence prior."}
aut_prev_rural_post <- do_jags_rand_model(x = aut_prev_rural_adj,
                              feat = "school_rurality",
                              model = rand_model,
                              theta_mu = aut_theta_mu_prior,
                              theta_sigma = aut_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("school_rurality" = "Feat_names")

plot_post_density(aut_prev_rural_post, aut_prev_rural_adj, 
                  feat = "school_rurality", 
                  theta_mu = aut_theta_mu_prior, theta_sigma = aut_theta_sigma_prior,
                  disease = "Autism")
```

```{r bayes rurality adhd, fig.cap = "Posterior predictive distribution for ADHD with a random effect on school's rurality, and with age- and sex-adjusted global prevalence prior."}
adhd_prev_rural_post <- do_jags_rand_model(x = adhd_prev_rural_adj,
                              feat = "school_rurality",
                              model = rand_model,
                              theta_mu = adhd_theta_mu_prior,
                              theta_sigma = adhd_theta_sigma_prior,
                              pars = pars, 
                              convergence_checks = FALSE) %>%
  rename("school_fee" = "Feat_names")

plot_post_density(adhd_prev_econA_post, adhd_prev_econA_adj, 
                  feat = "school_fee", 
                  theta_mu = adhd_theta_mu_prior, theta_sigma = adhd_theta_sigma_prior,
                  disease = "ADHD")
```


## Bayesian prevalence projection


```{r new prev arauc}
araucS_lower_prev <- aut_prev_health_adj %>%
  filter(health_service_name == "Araucanía Sur") %>%
  select(adjusted_rate) %>% as.numeric
araucS_upper_prev <- n_aut_araucS / aut_prev_health_adj %>%
  filter(health_service_name == "Araucanía Sur") %>%
  select(sum_sample_pop_size) %>% as.numeric
prev_delta <- araucS_upper_prev - araucS_lower_prev

araucS_lower <- aut_prev_health_adj %>%
  filter(health_service_name == "Araucanía Sur") %>%
  select(adjusted_count) %>% as.numeric
araucS_upper <- n_aut_araucS
araucS_mean <- (araucS_upper + araucS_lower) / 2
araucS_sd <- (araucS_upper - araucS_lower) / (2*1.96)

aut_prev_health_adj$new_rate <- numeric(nrow(aut_prev_health_adj))
aut_prev_health_adj$new_count <- numeric(nrow(aut_prev_health_adj))

for(i in 1:nrow(aut_prev_health_adj)) {
  if(aut_prev_health_adj$health_service_name[i] == "Servicio de Salud Araucanía Sur") {
    aut_prev_health_adj$new_rate[i] <- araucS_upper_prev
    aut_prev_health_adj$new_count[i] <- araucS_upper
  }
  else {
    aut_prev_health_adj$new_rate[i] <- aut_prev_health_adj$adjusted_rate[i] + prev_delta
    aut_prev_health_adj$new_count[i] <- round(aut_prev_health_adj$new_rate[i] * aut_prev_health_adj$sum_sample_pop_size[i], 0)
  }
}

```


```{r new prev health, include = FALSE}

# Need to do all by health service code not name because name sorts in different orders.

# Now have health service specific priors so need to provide them as vectors and index each as needed
rand_model_new <- "model {
  for(i in 1:nFeat) { # For each category in the feature grouping
    theta[i] ~ dbeta(theta_a[i], theta_b[i])
    disease_sample[i] ~ dbin(theta[i], nObs[i])
    disease_pred[i] ~ dbin(theta[i], nObs[i])
  }
}"

nFeat <- length(unique(aut_prev_health_adj$health_service_code))
FeatNames <- sort(unique(aut_prev_health_adj$health_service_code))

pars <- c("theta_a", "theta_b", "theta", "disease_sample", "disease_pred")

# Define beta prior
theta_mu <- (aut_prev_health_adj$new_rate + aut_prev_health_adj$adjusted_rate) / 2
theta_sigma <- (aut_prev_health_adj$new_rate - aut_prev_health_adj$adjusted_rate) / (2*1.96)
theta_a <- theta_mu * (theta_mu * (1-theta_mu) / theta_sigma^2 - 1)
theta_b <- (1 - theta_mu) * (theta_mu * (1-theta_mu) / theta_sigma^2 - 1)

#x <- seq(0,1, by =0.01)
#for(i in 1:29) {
#  plot(x, dbeta(x, theta_a[i], theta_b[i]), type = "l", xlim = c(0,0.1))
#}

# Initial values for model chains
rand_ini <- list(list(theta = rep(0.001, nFeat)),
                 list(theta = rep(0.01, nFeat)))
# Run JAGS model
rand_data <- list(theta_a = theta_a,
                  theta_b = theta_b,
                  nObs = aut_prev_health_adj$sum_sample_pop_size,
                  aut_sample = aut_prev_health_adj$adjusted_count,
                  nFeat = nFeat)
rand_jag <- jags.model(textConnection(rand_model_new),
                       data = rand_data,
                       inits = rand_ini,
                       n.chains = 2,
                       quiet = TRUE)
update(rand_jag, n.iter = nBurn)
rand_sam <- coda.samples(model = rand_jag,
                         variable.names = pars,
                         n.iter = nIter)

convergence_check <- FALSE
if(convergence_check) {
  print(mcmc_trace(rand_sam, paste0("theta[", 1:nFeat, "]"))) # Convergence looks fine and rhats <= 1.1
  print(mcmc_trace(rand_sam, paste0("disease_pred[", 1:nFeat, "]"))) # Convergence looks fine and rhats <= 1.1
  rand_summ <- summary(subset_draws(as_draws(rand_sam), pars),
                           ~quantile(.x, probs=c(0.025, 0.5, 0.975)),
                           ~mcse_quantile(.x, probs=c(0.025, 0.5, 0.975)),
                           "rhat") %>%
        arrange(desc(rhat))
  print(rand_summ)
}

aut_prev_health_post_new <- as_tibble(as_draws_matrix(rand_sam), rownames = "Iteration") %>%
    select(c("Iteration", contains("theta["))) %>%
    pivot_longer(cols = contains("theta["),
                 names_to = "health_service_code",
                 values_to = "predicted_prev") %>%
    mutate(Feat_names = factor(health_service_code, levels = c(paste0("theta[",1:nFeat,"]")), labels = FeatNames)) %>%
    select(Iteration, Feat_names, predicted_prev) %>%
  rename(health_service_code = Feat_names) %>%
  merge(health_service_lookup, by = "health_service_code") %>%
  rename(health_service_name_long = health_service_name,
         health_service_name = health_service_name_short)
  

# Plot manually because we need different CI's now
aut_prev_health_post_new_ci <- aut_prev_health_post_new %>%
  group_by(health_service_name) %>%
  summarise(post_lower = quantile(predicted_prev, 0.025),
            post_upper = quantile(predicted_prev, 0.975))
  
ggplot() +
  geom_density(data = aut_prev_health_post_new, aes(x = predicted_prev)) +
  geom_vline(data = aut_prev_health_post_new_ci, aes(xintercept = post_lower), color = "blue", linetype = "dotted") +
  geom_vline(data = aut_prev_health_post_new_ci, aes(xintercept = post_upper), color = "blue", linetype = "dotted") +
  geom_vline(data = aut_prev_health_adj, aes(xintercept = adjusted_rate), color = "red", linetype = "dashed") +
  geom_vline(data = aut_prev_health_adj, aes(xintercept = new_rate), color = "red", linetype = "dashed") +
  facet_wrap(~health_service_name) +
  labs(title = "Region specific priors informed by clinical data from Araucanía Sur",
       x = "Posterior predictive distribution",
       y = "Density")

```


```{r new prev health uniform prior}

####### Need to do all by health service code not name because name sorts in different orders.

# Now have health service specific priors so need to provide them as vectors and index each as needed
# OR Uniform prior https://stats.stackexchange.com/questions/555260/how-to-set-prior-for-bayesian-analysis 
rand_model_new <- "model {
  for(i in 1:nFeat) { # For each category in the feature grouping
    theta[i] ~ dunif(theta_lower[i], theta_upper[i])     #dbeta(theta_a[i], theta_b[i])
    disease_sample[i] ~ dbin(theta[i], nObs[i])
    disease_pred[i] ~ dbin(theta[i], nObs[i])
    #theta_a[i] <- theta_mu * (theta_mu * (1-theta_mu) / pow(theta_sigma, 2) - 1)
    #theta_b[i] <- (1 - theta_mu) * (theta_mu * (1-theta_mu) / pow(theta_sigma, 2) - 1)
  }
  #theta_mu ~ dunif(0, 1)
  #theta_sigma ~ dexp(1)
}"

# Increase burn in and iterations to get more precise predictions
nIter <- 2000
nBurn <- 2000
nFeat <- length(unique(aut_prev_health_adj$health_service_code))
FeatNames <- sort(unique(aut_prev_health_adj$health_service_code))

pars <- c("theta", "disease_sample", "disease_pred")

# Define uniform prior
theta_lower <- aut_prev_health_adj$adjusted_rate
theta_upper <- aut_prev_health_adj$new_rate

# Initial values for model chains
rand_ini <- list(list(theta = rep(0.001, nFeat)),
                 list(theta = rep(0.01, nFeat)))
# Run JAGS model
rand_data <- list(theta_lower = theta_lower,
                  theta_upper = theta_upper,
                  nObs = aut_prev_health_adj$sum_sample_pop_size,
                  aut_sample = aut_prev_health_adj$adjusted_count,
                  nFeat = nFeat)
rand_jag <- jags.model(textConnection(rand_model_new),
                       data = rand_data,
                       inits = rand_ini,
                       n.chains = 2,
                       quiet = TRUE)
update(rand_jag, n.iter = nBurn)
rand_sam <- coda.samples(model = rand_jag,
                         variable.names = pars,
                         n.iter = nIter)

convergence_check <- FALSE
if(convergence_check) {
  print(mcmc_trace(rand_sam, paste0("theta[", 1:nFeat, "]"))) # Convergence looks fine and rhats <= 1.1
  print(mcmc_trace(rand_sam, paste0("disease_pred[", 1:nFeat, "]"))) # Convergence looks fine and rhats <= 1.1
  rand_summ <- summary(subset_draws(as_draws(rand_sam), pars),
                           ~quantile(.x, probs=c(0.025, 0.5, 0.975)),
                           ~mcse_quantile(.x, probs=c(0.025, 0.5, 0.975)),
                           "rhat") %>%
        arrange(desc(rhat))
  print(rand_summ)
}

aut_prev_health_post_new <- as_tibble(as_draws_matrix(rand_sam), rownames = "Iteration") %>%
    select(c("Iteration", contains("theta["))) %>%
    pivot_longer(cols = contains("theta["),
                 names_to = "health_service_code",
                 values_to = "predicted_prev") %>%
    mutate(Feat_names = factor(health_service_code, levels = c(paste0("theta[",1:nFeat,"]")), labels = FeatNames)) %>%
    select(Iteration, Feat_names, predicted_prev) %>%
  rename(health_service_code = Feat_names) %>%
  merge(health_service_lookup, by = "health_service_code") %>%
  rename(health_service_name_long = health_service_name,
         health_service_name = health_service_name_short)
  

# Plot manually because we need different CI's now
aut_prev_health_post_new_ci <- aut_prev_health_post_new %>%
  group_by(health_service_name) %>%
  summarise(post_lower = quantile(predicted_prev, 0.025),
            post_upper = quantile(predicted_prev, 0.975))
  
ggplot() +
  geom_density(data = aut_prev_health_post_new, aes(x = predicted_prev)) +
  geom_vline(data = aut_prev_health_post_new_ci, aes(xintercept = post_lower), color = "blue", linetype = "dotted") +
  geom_vline(data = aut_prev_health_post_new_ci, aes(xintercept = post_upper), color = "blue", linetype = "dotted") +
  geom_vline(data = aut_prev_health_adj, aes(xintercept = adjusted_rate), color = "red", linetype = "dashed") +
  geom_vline(data = aut_prev_health_adj, aes(xintercept = new_rate), color = "red", linetype = "dashed") +
  facet_wrap(~health_service_name) +
  labs(title = "Region specific priors informed by clinical data from Araucanía Sur",
       x = "Posterior predictive distribution",
       y = "Density")

```

Red is the prior 95% CI (adjusted sample rate and it + prev_delta), blue is posterior 95% CrI

## MCA

```{r MCA patients small}
patients_mca_small <- clinical_small_raw %>% 
  rename("rurality" = "procedence",
         "dob" = "fecha_nacimiento",
         "apt_date" = "fecha_ejecutada",
         "type_appointment" = "appoinment") %>%
  mutate(gender = str_to_title(gender),
         autism = ifelse(cod_dg_1 %in% aut_codes | 
                           cod_dg_2 %in% aut_codes | 
                           cod_dg_3 %in% aut_codes, 1, 0),
         aut_rank = ifelse(cod_dg_1 %in% aut_codes, 1,
                    ifelse(cod_dg_2 %in% aut_codes, 2,
                    ifelse(cod_dg_3 %in% aut_codes, 3, NA))),
         intdisab = ifelse(cod_dg_1 %in% intdisab_codes | 
                           cod_dg_2 %in% intdisab_codes | 
                           cod_dg_3 %in% intdisab_codes, 1, 0),
         age_june30 = trunc(time_length(interval(ymd(dob), ymd("2021-06-30")), unit = "year")),
         commune_name_upper = ifelse(comuna == "CHOL CHOL", "CHOLCHOL",
                        ifelse(comuna == "CURACAUTIN", "CURACAUTÍN", 
                        ifelse(comuna == "PITRUFQUEN", "PITRUFQUÉN", 
                        ifelse(comuna == "PUCON", "PUCÓN", 
                        ifelse(comuna == "TOLTEN", "TOLTÉN", 
                        ifelse(comuna == "VILCUN", "VILCÚN", 
                        ifelse(comuna == "DIEGO DE ALMAGRO  (#)", "DIEGO DE ALMAGRO",
                        ifelse(comuna == "MACHALI", "MACHALÍ",
                        ifelse(comuna == "TEMUCO (##)", "TEMUCO", comuna))))))))),
         ses_status = ifelse(socio_economic_level %in% c("COLMENA GOLDEN CROSS", "RIO BLANCO", "CARABINEROS (DIPRECA)", "BANMEDICA S.A.", "PARTICULAR (SIN PREVISION)", "VIDA TRES"), "Private Health Insurance", socio_economic_level),
         ethnicity = ifelse(ethnicity == "CHILENO", "Chilean",
                     ifelse(ethnicity == "MAPUCHE", "Mapuche",
                     ifelse(ethnicity == "EXTRANJERO", "Foreign", "No ethnicity information"))),
         ethnicity = ifelse(is.na(ethnicity), "No ethnicity information", ethnicity), # for some reason the NA fix doesn't work in preceding line
         disability = ifelse(is.na(disability), "No disability information", disability),
         foster_care = ifelse(is.na(foster_care), "No foster care information", foster_care),
         medical_specialty_english = ifelse(medical_specialty == "Physiatry", "Psychiatry",
                                     ifelse(medical_specialty == "PEDIATRIA", "Paediatrics",
                                     ifelse(medical_specialty == "PSIQUIATRIA", "Psychiatry",
                                     ifelse(medical_specialty == "NEUROLOGIA", "Neurology", medical_specialty)))),
         medical_specialty_grouped = ifelse(medical_specialty_english %in% c("Psychiatry", "Child Psychiatry"), "Psychiatry",
                                     ifelse(medical_specialty_english %in% c("Neurology", "Pediatric Neurology"), "Neurology",
                                     ifelse(medical_specialty_english == "Paediatrics", "Paediatrics", "Other specialty"))),
         ) %>%
  left_join(region_service_commune_lookup, by = "commune_name_upper") %>%
  group_by(id, gender, age_june30) %>%
  summarise(ses_status = get.min.na(ses_status), # Fortunately the available values are in alphabetical order by status
            autism = get.max.na(autism),
            intdisab = get.max.na(intdisab),
            medical_specialty_grouped = get.mode(medical_specialty_grouped), # Most common medical specialty across visits
            hospital = hospital[which.max(apt_date)], # most recent hospital
            commune_name = commune_name[which.max(apt_date)],
            rurality = get.mode(rurality),
            ethnicity = get.mode(ethnicity),
            disability = get.yes.disability(disability),
            foster_care = get.yes.fostercare(foster_care)
            ) %>%
  ungroup() %>% 
  rename("sex_desc" = "gender",
         "age" = "age_june30") %>%
  mutate(sex_desc = as.factor(sex_desc),
         age_group = as.factor(ifelse(age <= 2, "Age 0-2", 
                               ifelse(age >= 3 & age <= 5, "Age 3-5",
                               ifelse(age >=6 & age <= 8, "Age 6-8", 
                               ifelse(age >=9 & age <=11, "Age 9-11", 
                               ifelse(age >=12 & age <= 14, "Age 12-14", 
                               ifelse(age >= 15 & age <= 18, "Age 15-18", "Adult"))))))), # Shouldn't be any adults in this dataset
         age = as.factor(age),
         commune_name = as.factor(commune_name),
         ses_status = as.factor(ses_status),
         rurality = as.factor(rurality),
         ethnicity = as.factor(ethnicity),
         disability_imp = as.factor(ifelse(disability == "No disability information", "No disability", disability)),
         disability = as.factor(disability),
         foster_care_imp = as.factor(ifelse(foster_care == "No foster care information", "No foster care", foster_care)),
         foster_care = as.factor(foster_care),
         autism = as.factor(autism),
         intdisab = as.factor(intdisab),
         medical_specialty_grouped = as.factor(medical_specialty_grouped),
         hospital = as.factor(hospital))
```

```{r MCA no imp}
patients_mca_noimp <- patients_mca_small %>%
  #filter(autism == 1) %>%
   select(#id,
          sex_desc,
          age,
          #age_group,
          autism,
          commune_name,
          #hospital, # Don't use hospital because in the small dataset they are all from Villarrica Hospital
          #medical_specialty_grouped,
          #intdisab,
          ses_status,
          rurality,
          ethnicity,
          disability,
          #disability_imp,
          foster_care#,
          #foster_care_imp
          )

v_colours =  viridis(10, option = "G")
  
res_mca_patients_noimp <- FactoMineR::MCA(patients_mca_noimp, # Can only take categorical variables and they have to be cast to factors
                                    ncp = 9, # Needs to match number of features
                                    graph = FALSE) 

# Plot features
fviz_mca_var(res_mca_patients_noimp, choice = "mca.cor", 
            repel = TRUE, # Avoid text overlapping
            ggtheme = theme_minimal())

# Plot categories
fviz_mca_var(res_mca_patients_noimp,
             #habillage = grp,
             col.var = "contrib",
             #gradient.cols = c("#39568C", "#3CBB75", "#DCE319"),
             gradient.cols = c(v_colours[1], v_colours[5], v_colours[7]),
             repel = TRUE, # Avoid text overlapping (slow if many points)
             ggtheme = theme_minimal())

# Plot individual patients
# fviz_mca_ind(res_mca_patients_noimp, 
#              label = "none",
#              #col.ind = "cos2", 
#              #gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
#              addEllipses = TRUE,
#              ellipse.level = 0.95,
#              repel = FALSE, # Graphs is not meaningful if this is TRUE
#              ggtheme = theme_minimal())
# OR
mca_noimp_sex_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "sex_desc", # color by groups 
             #palette = c("green", "blue"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by sex",
             ggtheme = theme_minimal()) 
mca_noimp_age_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "age", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by age",
             ggtheme = theme_minimal()) +
  theme(legend.position = "none")
mca_noimp_aut_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "autism", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by autism status",
             ggtheme = theme_minimal()) 
mca_noimp_commune_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "commune_name", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by commune of residence",
             ggtheme = theme_minimal()) + #Really not meaningful
  theme(legend.position = "none")
mca_noimp_ses_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "ses_status", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by SES status",
             ggtheme = theme_minimal()) 
mca_noimp_rural_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "rurality", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by rurality",
             ggtheme = theme_minimal())
mca_noimp_ethnic_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "ethnicity", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by ethnicity",
             ggtheme = theme_minimal())
mca_noimp_disab_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "disability", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by disability status",
             ggtheme = theme_minimal())
mca_noimp_foster_plot <- fviz_mca_ind(res_mca_patients_noimp, 
             label = "none", # hide individual labels
             habillage = "foster_care", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by foster care status",
             ggtheme = theme_minimal())

grid.arrange(mca_noimp_sex_plot, mca_noimp_age_plot, mca_noimp_aut_plot,
             mca_noimp_commune_plot, mca_noimp_ses_plot, mca_noimp_rural_plot,
             mca_noimp_ethnic_plot, mca_noimp_disab_plot, mca_noimp_foster_plot, ncol = 3, nrow = 3)

#fviz_ellipses(res_mca_patients, 1:4, geom = "point") # Ugly and too many warnings
#fviz_ellipses(res_mca_patients, c("sex_desc", "age_group", "ses_status"), geom = "point")
#fviz_ellipses(res_mca_patients, 1, geom = "point")

#fviz_cos2(res_mca_patients_noimp, choice = "var", axes = 1:2, xtickslab.rt = 90)
#round(res_mca_patients_noimp$var$contrib,2) # "The variable categories with the larger value, contribute the most to the definition of the dimensions. Variable categories that contribute the most to Dim.1 and Dim.2 are the most important in explaining the variability in the data set."

# Contributions of variable categories to dimension 1
#fviz_contrib(res_mca_patients_noimp, choice = "var", axes = 1, top = 15) 
# Contributions of variable categories to dimension 2
#fviz_contrib(res_mca_patients_noimp, choice = "var", axes = 2, top = 15)
# Total contribution to dimension 1 and 2
#fviz_contrib(res_mca_patients_noimp, choice = "var", axes = 1:2, top = 15)
# "The red dashed line on the graph above indicates the expected average value, If the contributions were uniform" See http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/114-mca-multiple-correspondence-analysis-in-r-essentials/ for calculations


```

```{r MCA imp}
patients_mca_imp <- patients_mca_small %>%
  #filter(autism == 1) %>%
   select(#id,
          sex_desc,
          age,
          #age_group,
          autism,
          commune_name,
          #hospital, # Don't use hospital because in the small dataset they are all from Villarrica Hospital
          #medical_specialty_grouped,
          #intdisab,
          ses_status,
          rurality,
          ethnicity,
          #disability,
          disability_imp,
          #foster_care,
          foster_care_imp
          )
# Note we still have more than 1 row for some patients because they have multiple communes, could go with their most recent commune
# We have 416 rows and 406 patients
  
res_mca_patients_imp <- FactoMineR::MCA(patients_mca_imp, # Can only take categorical variables and they have to be cast to factors
                                    ncp = 9, # Needs to match number of features
                                    graph = FALSE) 

# Plot features
fviz_mca_var(res_mca_patients_imp, choice = "mca.cor", 
            repel = TRUE, # Avoid text overlapping
            ggtheme = theme_minimal())

# Plot categories
fviz_mca_var(res_mca_patients_imp,
             #habillage = grp,
             col.var = "contrib",
             #gradient.cols = c("#39568C", "#3CBB75", "#DCE319"),
             gradient.cols = c(v_colours[1], v_colours[5], v_colours[7]),
             repel = TRUE, # Avoid text overlapping (slow if many points)
             ggtheme = theme_minimal())

# Plot individual patients
# fviz_mca_ind(res_mca_patients_noimp, 
#              label = "none",
#              #col.ind = "cos2", 
#              #gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
#              addEllipses = TRUE,
#              ellipse.level = 0.95,
#              repel = FALSE, # Graphs is not meaningful if this is TRUE
#              ggtheme = theme_minimal())
# OR
mca_imp_sex_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "sex_desc", # color by groups 
             #palette = c("green", "blue"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by sex",
             ggtheme = theme_minimal()) 
mca_imp_age_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "age", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by age",
             ggtheme = theme_minimal()) +
  theme(legend.position = "none")
mca_imp_aut_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "autism", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by autism status",
             ggtheme = theme_minimal()) 
mca_imp_commune_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "commune_name", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by commune of residence",
             ggtheme = theme_minimal()) + #Really not meaningful
  theme(legend.position = "none")
mca_imp_ses_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "ses_status", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by SES status",
             ggtheme = theme_minimal()) 
mca_imp_rural_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "rurality", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by rurality",
             ggtheme = theme_minimal())
mca_imp_ethnic_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "ethnicity", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by ethnicity",
             ggtheme = theme_minimal())
mca_imp_disab_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "disability_imp", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by disability status",
             ggtheme = theme_minimal())
mca_imp_foster_plot <- fviz_mca_ind(res_mca_patients_imp, 
             label = "none", # hide individual labels
             habillage = "foster_care_imp", # color by groups 
             #palette = c("#00AFBB", "#E7B800"),
             addEllipses = TRUE, ellipse.type = "confidence",
             title = "Patients by foster care status",
             ggtheme = theme_minimal())

grid.arrange(mca_imp_sex_plot, mca_imp_age_plot, mca_imp_aut_plot,
             mca_imp_commune_plot, mca_imp_ses_plot, mca_imp_rural_plot,
             mca_imp_ethnic_plot, mca_imp_disab_plot, mca_imp_foster_plot, ncol = 3, nrow = 3)

#fviz_ellipses(res_mca_patients, 1:4, geom = "point") # Ugly and too many warnings
#fviz_ellipses(res_mca_patients, c("sex_desc", "age_group", "ses_status"), geom = "point")
#fviz_ellipses(res_mca_patients, 1, geom = "point")

# fviz_cos2(res_mca_patients_imp, choice = "var", axes = 1:2, xtickslab.rt = 90)
# round(res_mca_patients_imp$var$contrib,2) # "The variable categories with the larger value, contribute the most to the definition of the dimensions. Variable categories that contribute the most to Dim.1 and Dim.2 are the most important in explaining the variability in the data set."
# 
# # Contributions of variable categories to dimension 1
# fviz_contrib(res_mca_patients_imp, choice = "var", axes = 1, top = 15) 
# # Contributions of variable categories to dimension 2
# fviz_contrib(res_mca_patients_imp, choice = "var", axes = 2, top = 15)
# # Total contribution to dimension 1 and 2
# fviz_contrib(res_mca_patients_imp, choice = "var", axes = 1:2, top = 15)
# # "The red dashed line on the graph above indicates the expected average value, If the contributions were uniform" See http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/114-mca-multiple-correspondence-analysis-in-r-essentials/ for calculations


```

# Supplementary materials


```{r adj prev plot aut age, fig.cap = "Sample prevalence of autism by age and sex. Bars show 95% normal confidence intervals."}
# Autism
aut_prev.age.sex <- get_grouped_prev_plot(x = chile_bayes_aut, 
                                          grouping_vars = c("age_june30", "sex_desc", "autism"),
                                          disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

# By age and sex
ggplot(data = aut_prev.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  labs(title = "Autism prevalence",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")

```


```{r adj prev plot adhd age, fig.cap = "Sample prevalence of ADHD by age and sex. Bars show 95% normal confidence intervals."}
# ADHD
adhd_prev.age.sex <- get_grouped_prev_plot(x = chile_bayes_adhd, 
                                          grouping_vars = c("age_june30", "sex_desc", "adhd"),
                                          disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

# By age and sex
ggplot(data = adhd_prev.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  labs(title = "ADHD prevalence",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")

```


```{r adj prev health plot aut age, fig.cap = "Sample prevalence of autism by health service, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
aut_prev_health.age.sex <- get_grouped_prev_plot(x = chile_bayes_aut, 
                                                 grouping_vars = c("health_service_name", "age_june30", "sex_desc", "autism"),
                                                 disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_health.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~health_service_name) +
  labs(title = "Autism prevalence by health service",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev health plot adhd age, fig.cap = "Sample prevalence of ADHD by health service, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
adhd_prev_health.age.sex <- get_grouped_prev_plot(x = chile_bayes_adhd, 
                                                 grouping_vars = c("health_service_name", "age_june30", "sex_desc", "adhd"),
                                                 disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_health.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~health_service_name) +
  labs(title = "ADHD prevalence by health service",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev araucS plot aut age, fig.cap = "Sample prevalence of autism by commune in Araucanía Sur health service, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
aut_prev_araucS.age.sex <- get_grouped_prev_plot(x = chile_bayes_aut_araucS, 
                                                 grouping_vars = c("commune_name", "age_june30", "sex_desc", "autism"),
                                                 disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_araucS.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~commune_name) +
  labs(title = "Autism prevalence by commune in Araucanía Sur",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev economicAll plot aut age, fig.cap = "Sample prevalence of autism by socio-economic (SES) status of student's family, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
aut_prev_econA.age.sex <- get_grouped_prev_plot(x = chile_bayes_aut, 
                                                 grouping_vars = c("school_fee", "age_june30", "sex_desc", "autism"),
                                                 disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_econA.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_fee) +
  labs(title = "Autism prevalence by SES status",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev economicAll plot adhd age, fig.cap = "Sample prevalence of ADHD by socio-economic (SES) status of student's family, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
adhd_prev_econA.age.sex <- get_grouped_prev_plot(x = chile_bayes_adhd, 
                                                 grouping_vars = c("school_fee", "age_june30", "sex_desc", "adhd"),
                                                 disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_econA.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_fee) +
  labs(title = "ADHD prevalence by SES status",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev ethnicity plot aut age, fig.cap = "Sample prevalence of autism by ethnicity, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
aut_prev_ethnic.age.sex <- get_grouped_prev_plot(x = chile_bayes_aut, 
                                                 grouping_vars = c("ethnic_2_group", "age_june30", "sex_desc", "autism"),
                                                 disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_ethnic.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~ethnic_2_group) +
  labs(title = "Autism prevalence by ethnicity",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev ethnicity plot adhd age, fig.cap = "Sample prevalence of ADHD by ethnicity, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
adhd_prev_ethnic.age.sex <- get_grouped_prev_plot(x = chile_bayes_adhd, 
                                                 grouping_vars = c("ethnic_2_group", "age_june30", "sex_desc", "adhd"),
                                                 disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_ethnic.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~ethnic_2_group) +
  labs(title = "ADHD prevalence by ethnicity",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev rurality plot aut age, fig.cap = "Sample prevalence of autism by school's rurality, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
aut_prev_rural.age.sex <- get_grouped_prev_plot(x = chile_bayes_aut, 
                                                 grouping_vars = c("school_rurality", "age_june30", "sex_desc", "autism"),
                                                 disease = "autism") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = aut_prev_rural.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_rurality) +
  labs(title = "Autism prevalence by school's rurality",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```


```{r adj prev rurality plot adhd age, fig.cap = "Sample prevalence of ADHD by school's rurality, age and sex. Bars show 95% normal confidence intervals."}
# Single ages
adhd_prev_rural.age.sex <- get_grouped_prev_plot(x = chile_bayes_adhd, 
                                                 grouping_vars = c("school_rurality", "age_june30", "sex_desc", "adhd"),
                                                 disease = "adhd") %>%
  mutate(ci_lower = ifelse(ci_lower < 0, 0, ci_lower))

ggplot(data = adhd_prev_rural.age.sex) +
  geom_col(aes(x = sex_desc, y = sample_prevalence, group = age_june30, fill = age_june30), position = position_dodge()) +
  geom_errorbar(aes(x = sex_desc, ymin = ci_lower, ymax = ci_upper, group = age_june30), width = 0.2, position = position_dodge(width = 0.9)) +
  scale_fill_viridis_c(option = "plasma") +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2)) +
  facet_wrap(~school_rurality) +
  labs(title = "ADHD prevalence by school's rurality",
       x = "Sex",
       y = "Sample prevalence",
       fill = "Age")
```



